---
title: "Carbon Chemestry explore - New database"
author: "Ana Palacio-Castro"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 8
    df_print: paged
    toc: yes
    toc_float: true
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, options(knitr.kable.NA = ''))
```

# Libraries and settings

```{r, include=FALSE}
# Libraries
    library(plyr)
    library(tidyverse)
    library(reshape2)
    library(lubridate)
    library(knitr)
    library(dplyr)
    library(broom)

    library(ggpubr)
    library(ggthemes)
    library(gridExtra)
    library(ggExtra)
    
# Interactive Maps
    library(leaflet)

# Plots
MyTheme<-theme_bw() +  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )

```

# 1. Import and format carbon chemestry data

```{r, include=FALSE}
# 1. Get data
CC.data<-read.csv("Data/ws-mysql-v4.csv", header = T)
  #summary(CC.data)
  str((CC.data))
  summary(CC.data$Location)
  Sites<-as.data.frame(unique(CC.data$SiteID))
  #CC.data$SiteID[CC.data$SiteID=="LK"]<-"21LK"
  CC.data$SiteID[CC.data$SiteID=="WS cruise"]<-"WS"
  # Sites<-as.data.frame(unique(CC.data$SiteID))
  
# 2. Format variables
  # Date/times
    # Year
    CC.data$Year<-as.numeric(CC.data$Year)
    summary(CC.data$Year)
    CC.data<-CC.data[!is.na(CC.data$Year),]
    
    # UTC Date
    CC.data$UTCDate<-as.Date(CC.data$UTCDate, "%m/%d/%Y", tz="UTC")
    summary(CC.data$UTCDate)
  
    # UTC Date-time 
    CC.data$UTCDate_Time<-paste(CC.data$UTCDate, CC.data$UTCTime, sep = " ")
    CC.data$UTCDate_Time<-as_datetime(CC.data$UTCDate_Time, tz="UTC")
    summary(CC.data$UTCDate_Time)
    
    # EST Date-time 
    CC.data$datetime<-as_datetime(CC.data$UTCDate_Time, tz="EST")
    CC.data$ESTDate<-as.Date(CC.data$datetime, tz="EST")
    CC.data$ESTTime <- format(CC.data$datetime,"%H:%M:%S")
   
    #CC.data$Month<-month(CC.data$ESTDate)
    CC.data$Month <- as.numeric(format(CC.data$ESTDate,"%m"))
    summary(CC.data$Month)
    CC.data$Month<-month.abb[CC.data$Month]
    #CC.data$Month<-factor(CC.data$Month, levels = month.name)
    CC.data$Month<-factor(CC.data$Month, 
                          levels = c("Apr", "May","Jun",
                                    "Jul", "Aug", "Sep",
                                    "Oct","Nov","Dec",
                                    "Jan", "Feb", "Mar"))
    
    CC.data$Months<-months(CC.data$ESTDate)
    CC.data$Months<-factor(CC.data$Months, levels = month.name)
    
  ## Add time variables 
    CC.data <- transform(CC.data,
                       SiteID = factor(SiteID),
                       MY = format(datetime, format = '%Y-%m'),
                       MoY = as.numeric(format(datetime, format = '%m')),
                       #DoY = as.numeric(format(datetime, format = '%j')),
                       ToD = as.numeric(format(datetime, format = '%H')) +
                         (as.numeric(format(datetime, format = '%M')) / 60))
    summary(CC.data)


   # Numerical data
    # CC.data$Latitude <-as.numeric((as.character(CC.data$Latitude)))
    # CC.data$Longitude <-as.numeric((as.character(CC.data$Longitude)))
   
    # CC.data$Temperature_C <-
    #    as.numeric((as.character(CC.data$Temperature_C)))
    # Temperature_NA2<-CC.data[(is.na(CC.data$Temperature_C)),]
  
    # CC.data$TA <-as.numeric((as.character(CC.data$TA)))
    # CC.data$DIC <-as.numeric((as.character(CC.data$DIC)))
    
    # CC.data$pH <-as.numeric((as.character(CC.data$pH)))
    # CC.data$pCO2 <-as.numeric((as.character(CC.data$pCO2)))
    # CC.data$Aragonite_Sat_W<-
    #   as.numeric((as.character(CC.data$Aragonite_Sat_W)))
```

Notes:
* duplicated labels LK and 21LK; WS and WS cruise

## Add seasonality

* Winter: Dec 20-March 19
* Spring: March 20-June 18
* Summer: June 19-Sep 20 
* Fall: Sep 21-Dec 19

```{r, include=FALSE}
# Define seasons (rougly by month)
  metseasons <- c(
    "01" = "Winter", "02" = "Winter", "03" = "Winter",
    "04" = "Spring", "05" = "Spring", "06" = "Spring",
    "07" = "Summer", "08" = "Summer", "09" = "Summer",
    "10" = "Fall", "11" = "Fall", "12" = "Fall"
  )
    Seasons<-as.data.frame(metseasons[format(CC.data$ESTDate, "%m")])
    colnames(Seasons)<-"Season"
    CC.data<-cbind(CC.data, Seasons)
    
    # Adjust byu days of the month
    CC.data$Season[(CC.data$Months=="March" & CC.data$DoM>19)]<-"Spring"
    CC.data$Season[(CC.data$Months=="June" & CC.data$DoM>19)]<-"Summer"
    CC.data$Season[(CC.data$Months=="September" & CC.data$DoM>21)]<-"Fall"
    CC.data$Season[(CC.data$Months=="December" & CC.data$DoM>20)]<-"Winter"
```

* Wet: May - October
* Dry: November - April

```{r, include=FALSE}

precipitation<-c(
    "01" = "Dry", "02" = "Dry", "03" = "Dry", "04" = "Dry",
    "05" = "Wet", "06" = "Wet", "07" = "Wet",
    "08" = "Wet", "09" = "Wet", "10" = "Wet",
    "11" = "Dry",  "12" = "Dry"
  )

Precipitation<-as.data.frame(precipitation[format(CC.data$ESTDate, "%m")])
    colnames(Precipitation)<-"Precipitation"
    CC.data<-cbind(CC.data, Precipitation)
```

## Subset only FK data 

* This removes samples from Gulf of Mexico
* Add reef zone: "Inshore", "Mid channel", "Offshore", "Oceanic"
* Add reef subregion: "BB", "UK", "MK", "LK"

```{r}
 #Get only FLK data#
  Metadata<-read.csv("Data/FLKLocations.csv", header = T)
  
  FLK.data<-join(CC.data, Metadata, 
                 type = "left", by="SiteID")
  str(FLK.data)
  
  FLK.data<-subset(FLK.data, FLK.data$Sub_region!="NA")
  
  FLK.data$Sub_region<-factor(FLK.data$Sub_region, levels = c(
                        "BB", "UK", "MK", "LK"))

  FLK.data$Zone<-factor(FLK.data$Zone, levels = c(
                        "Inshore", "Mid channel", 
                        "Offshore", "Oceanic"))
```

## Label known extreme events to check outliers 

```{r}
# Label and filter extreme events
  FLK.data$Extreme<-"Normal"
  FLK.data$Extreme[FLK.data$MY=="2010-03"] <-"ColdMortality"
  FLK.data$Extreme[FLK.data$MY=="2010-08"] <-"Waves/Overcast"
  FLK.data$Extreme[FLK.data$MY=="2011-10"] <-"LowSalinty"
  FLK.data$Extreme[FLK.data$MY=="2011-08"] <-"HighOmega_NoReason"
  FLK.data$Extreme<-as.factor(FLK.data$Extreme)
```

# 2. Check data available

## 2.1 Locations (all samples)

```{r MapINformation, include=FALSE}
Locations <- FLK.data %>% select(Latitude,
                                Longitude, 
                                Sub_region, 
                                SiteID)
#3Locations$GPS<-paste(Locations$Latitude,
                     #"-", 
                     #Locations$Longitude)
Locations<-unique(Locations)

pal.gen <- colorFactor(palette = "Set1",
                         domain = CC.data$Zone)
```


```{r AllMap, echo=FALSE}

# leaflet(FLK.data, height = '400px') %>%
#   addTiles() %>%
#   #addProviderTiles(providers$Esri.WorldImagery)%>%
#   addProviderTiles(providers$OpenStreetMap) %>%
#   #addMarkers(icon=coral.icon) %>%
#   addCircleMarkers(lng = ~Longitude, lat = ~Latitude,
#                    #stroke = TRUE,
#                    radius = 2,
#                    fillOpacity = 1,
#                    color = ~pal.gen(Zone),
#                    label = ~CTDID,
#                    labelOptions = labelOptions(
#                      noHide = F, direction = "bottom",
#                      textOnly = TRUE,
#                      style = list(
#         "color" = "white")))  %>%
#   addLegend(position = "topright",
#             pal = pal.gen,
#             values = ~Zone, opacity = 1) %>%
#   fitBounds(lng1=-81.20, lat=26, lng2=-80.5, lat2=24)

```

**Figure:** Map of the sites where individual samples were collected

**Notes:**
* Check location of individual SiteIDs

## 2.2 Average GPS point location

```{r WS.POINTS, include=FALSE}
WS.GPS.Sites <- ddply (FLK.data, .(Sub_region, Zone, SiteID),summarise,
                Lat = mean (Latitude, na.rm = T), 
                Lon = mean (Longitude, na.rm = T),
                number = n())
#write.csv(WS.GPS.Sites, "FLK_results/1_meanSatationGPS_v3.csv")
```

```{r}
# Coordinates<-select(FLK.data, "CTDID", "Latitude", "Longitude", "SiteID")
# Coordinates<-join(Coordinates, WS.GPS.Sites,
#                  type = "left", by="SiteID")
# Coordinates$Lat_diff<-abs(Coordinates$Latitude-Coordinates$Lat)
# Coordinates$Lon_diff<-abs(Coordinates$Longitude-Coordinates$Lon)
# Check.coordinates1<- Coordinates[(Coordinates$Lat_diff>0.02), ]
# Check.coordinates2<- Coordinates[(Coordinates$Lon_diff>0.02), ]
# Check.coordinates<- rbind(Check.coordinates1, Check.coordinates2)
# Check.coordinates<-unique(Check.coordinates)
#write.csv(Check.coordinates, "FLK_results/2_CheckGPS_points_v3.csv")
```


```{r Mean.Map, include=FALSE}
# Map information
pal.gen <- colorFactor(palette = "Set1",
                         domain = WS.GPS.Sites$Zone)
```

```{r WSmap, echo=FALSE}

# leaflet(WS.GPS.Sites, height = '600px') %>% 
#   addTiles() %>%
#   #addProviderTiles(providers$Esri.WorldImagery)%>%
#   addProviderTiles(providers$OpenStreetMap) %>% 
#   
#   # Sub_regions
#      addRectangles(
#       lng1=-80.26, lat1=25.7,
#       lng2=-80.02, lat2=25.25,
#       opacity = 1,
#       color = "black",
#       weight=1,
#       fillColor = "transparent",
#       label = "Biscayne Bay",
#       labelOptions = labelOptions(
#                        noHide = T, direction = "right",
#                        textOnly = F))  %>% 
#     addRectangles(
#       lng1=-80.6, lat1=25.20,
#       lng2=-80.2, lat2=24.8,
#       opacity = 1,
#       color = "black",
#       weight=1,
#       fillColor = "transparent",
#       label = "Upper Keys",
#       labelOptions = labelOptions(
#                        noHide = T, direction = "right",
#                        offset = c(20, 20),
#                        textOnly = F))  %>%
#   
#     addRectangles(
#       lng1=-81.11, lat1=24.85,
#       lng2=-80.61, lat2=24.55,
#       opacity = 1,
#       color = "black",
#       weight=1,
#       fillColor = "transparent",
#       label = "Middel Keys",
#       labelOptions = labelOptions(
#                        noHide = T, direction = "right",
#                         offset = c(15, 20),
#                        textOnly = F)) %>% 
#     addRectangles(
#       lng1=-81.88, lat1=24.34,
#       lng2=-81.14, lat2=24.72,
#       opacity = 1,
#       color = "black",
#       weight=1,
#       fillColor = "transparent",
#       label = "Lower Keys",
#       labelOptions = labelOptions(
#                        noHide = T, direction = "right",
#                          offset = c(20, 30),
#                        textOnly = F)) %>% 
#   #Stations  
#   addCircleMarkers(lng = ~Lon, lat = ~Lat, 
#                    stroke = FALSE, 
#                    radius = 4, 
#                    fillOpacity = 1,
#                    color = ~pal.gen(Zone),
#                    label = ~SiteID,
#                    labelOptions = labelOptions(
#                      noHide = F, direction = "bottom",
#                      textOnly = TRUE,
#                      style = list(
#         "color" = "white")))  %>%
#   
#   addLegend(position = "topright",
#             pal = pal.gen, 
#             values = ~Zone, opacity = 1) %>%
#   fitBounds(lng1=-81.20, lat=25.8, lng2=-80.5, lat2=24)
#   
```

**Figure:** Permanent location of WS stations

## 2.3 Number of samples

### By zone and location

```{r, echo=FALSE}
Cases_Loc_Zone<-FLK.data %>% count(Sub_region,
                                  Zone,
                                  sort = F)

Cases_Loc_Zone<-as.data.frame(Cases_Loc_Zone %>%
                   pivot_wider(names_from = Zone,
                   values_from = n))
#write.csv(Cases_Loc_Zone, "FLK_results/SampleS_Region_zone.csv")

kable(as.data.frame(Cases_Loc_Zone, format = "markdown"), 
      longtable = TRUE)
```

### By year and sub_region

```{r, echo=FALSE}
Cases_Reg_Year<-FLK.data %>% count(Year, Sub_region, sort = F)

Cases_Reg_Year<-as.data.frame(Cases_Reg_Year %>%
    pivot_wider(names_from = Year, values_from = n))
#write.csv(Cases_Reg_Year, "FLK_results/SampleS_Region_Year.csv")

kable(as.data.frame(Cases_Reg_Year, format = "html"),  caption = "Samples collected each year")
```

### By climatological season and region

```{r, echo=FALSE}
Cases_Reg_season<-FLK.data %>% count(Season, Sub_region, sort = T)

Cases_Reg_season<-as.data.frame(Cases_Reg_season %>%
    pivot_wider(names_from = Season, values_from = n))
#write.csv(Cases_Reg_season, "FLK_results/SampleS_RegionSeason.csv")

kable(as.data.frame(Cases_Reg_season, format = "html"),
      caption = "Samples collected in each seson")
```

### By Month-year

```{r, echo=FALSE}

Cases_Month<-FLK.data %>% count(Months,
                                Year,
                                sort = F)

Cases_Month<-as.data.frame(Cases_Month %>%
    pivot_wider(names_from = Year, values_from = n))

# Organize table
 Cases_Month<-Cases_Month %>% 
     select(sort(names(.)))

kable(as.data.frame(Cases_Month, format = "html"), caption="Samples collected by year-month")
#write.csv(Cases_Month, "FLK_results/SampleS_Month_Year.csv")
```

### By Month-region

```{r, echo=FALSE}

Cases_Month_Location<-FLK.data %>% count(Sub_region,
                                Zone,
                                Month, sort = F)

Cases_Month_Location<-as.data.frame(Cases_Month_Location %>%
    pivot_wider(names_from = Month, values_from = n))
#write.csv(Cases_Month_Location, "FLK_results/SampleS_Monthlocation.csv")

kable(as.data.frame(Cases_Month_Location, format = "html"),
      caption="Samples collected by month-location")
```

### Per station during all sampling time

```{r, echo=FALSE}
Cases_Site_FLK<-FLK.data %>% count(Year, SiteID, sort = F)
#Cases_Site_FLK

Cases_Site_FLK<-as.data.frame(Cases_Site_FLK %>%
    pivot_wider(names_from = Year, values_from = n))
#write.csv(Cases_Site_FLK, "FLK_results/SampleSiteIDFLK.csv")

kable(as.data.frame(Cases_Site_FLK, format = "html"),
      caption = "Samples collected in SiteIDs")
```

# 3. TA and DIC salinity normalization

## Salinity standarizations 

1. Use salinity Bottle first, if not available, salinity CTD

```{r, echo=FALSE}
# 1. Get the best salinity available. First bottle, if empy CTD
    FLK.data$BestSalinity<-FLK.data$Salinity_Bottle
    
    FLK.data$BestSalinity<-ifelse(is.na(FLK.data$Salinity_Bottle),
                                 FLK.data$Salinity_CTD,
                                 FLK.data$Salinity_Bottle)
    MeanSalinity<-mean(FLK.data$BestSalinity)
    
# 2. TA and DIC 35 normalization
    FLK.data$n35TA<-(FLK.data$TA_umol_kg/FLK.data$BestSalinity)*MeanSalinity
    FLK.data$n35DIC<-(FLK.data$DIC_umol_kg/FLK.data$BestSalinity)*MeanSalinity
```

2. Calculate TA intercepts

```{r}

# TA_coef <- FLK.data %>% 
#                 group_by(Region) %>%
#                 do({model = lm(TA_umol_kg~BestSalinity, data=.)  # model
#                     data.frame(tidy(model), # get coefficient info
#                     glance(model))})        # get model info
    
 TA_coef <- FLK.data[FLK.data$Zone=="Oceanic",] %>% 
                 group_by(Region) %>%
                 do({model = lm(TA_umol_kg~BestSalinity, data=.)  # model
                     data.frame(tidy(model), # get coefficient info
                     glance(model))})        # get model info
    
```

3. Calculate DIC intercepts 

```{r}
    DIC_coef <- FLK.data[FLK.data$Zone=="Oceanic",] %>% 
                  group_by(Region) %>%
                  do({model = lm(DIC_umol_kg~BestSalinity, data=.)  
                  # create model
                  data.frame(tidy(model), # get coefficient info
                  glance(model))})        # get model info

    # DIC_coef <- FLK.data %>% 
    #               group_by(Region) %>%
    #               do({model = lm(DIC_umol_kg~BestSalinity, data=.)  
    #               # create model
    #               data.frame(tidy(model), # get coefficient info
    #               glance(model))})        # get model info
```

4. Normalize with Friss equation

```{r}
# 4. Normalize the data
  TA_TO<-subset(TA_coef, term=="(Intercept)")
  TA_TO<-as.data.frame(select(TA_TO, c(Region, estimate)))
  names(TA_TO)[2] <- "TA_0"
  
  DIC_TO<-subset(DIC_coef, term=="(Intercept)")
  DIC_TO<-as.data.frame(select(DIC_TO, c(Region, estimate)))
  names(DIC_TO)[2] <- "DIC_0"
    
  Intercepts<-join(TA_TO, DIC_TO, by="Region", type="full")
  FLK.data<-join(FLK.data, Intercepts, by="Region", type="left")
```

```{r}
FLK.data$nTA<-(
    (FLK.data$TA_umol_kg-FLK.data$TA_0)/
    FLK.data$BestSalinity)*MeanSalinity+FLK.data$TA_0

  FLK.data$nDIC<-(
    (FLK.data$DIC_umol_kg-FLK.data$DIC_0)/
    FLK.data$BestSalinity)*MeanSalinity+FLK.data$DIC_0
  
#write.csv(FLK.data, "FLK_results/FLK.data_normalized.csv", row.names = F)
```

5. TA parameters to nTA

```{r}
kable(as.data.frame(TA_coef[,1:8], format = "markdown"), 
      caption = "TA parameters for normalization", digits = 3)
#write.csv(TA_coef, "TA_coef.csv")

```
    
```{r, fig.height=8.8, fig.width=8.8}
# 5. Chech normalization?
#nTA_Sal<- ggplot(FLK.data[FLK.data$Zone=="Oceanic",] ) + theme_bw() +
  
nTA_Sal<- ggplot(FLK.data) + MyTheme+
facet_grid(~Zone)+
 
  geom_point(aes (BestSalinity, TA_umol_kg, fill=Season), alpha=0.5, shape=21)+
  geom_smooth(aes(BestSalinity, TA_umol_kg), linetype=2, method = "lm", color="black")+
    
  geom_point(aes (BestSalinity, nTA, fill=Season), alpha=0.5, shape=24)+
  geom_smooth(aes(BestSalinity, nTA), linetype=1, method = "lm")
    
  #geom_point(aes (BestSalinity, n35TA, fill=Season), alpha=0.5, shape=25)+
  #geom_smooth(aes(BestSalinity, n35TA), linetype=3, method = "lm")+  

#nTA_Sal
#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

6. DIC parameters to nDIC

```{r}
kable(as.data.frame(DIC_coef[,1:8], format = "markdown"), 
      caption = " DIC parameters for normalization", digits = 3)

#write.csv(DIC_coef, "DIC_coef.csv")
    
```

```{r, fig.height=8.8, fig.width=8.8}
nDIC_Sal<- ggplot(FLK.data) + MyTheme+
  facet_grid(~Zone)+
#nDIC_Sal<-ggplot(FLK.data[FLK.data$Zone=="Oceanic",] ) + theme_bw() +
  geom_point(aes (BestSalinity, DIC_umol_kg, fill=factor(Season)),
             alpha=0.5, shape=21)+
  geom_smooth(aes(BestSalinity, DIC_umol_kg),
              linetype=2, method = "lm", color="black")+
    
  geom_point(aes (BestSalinity, nDIC, fill=factor(Season)), alpha=0.5, shape=24)+
  geom_smooth(aes(BestSalinity, nDIC), linetype=1, method = "lm")
#nDIC_Sal

#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

```{r}

FLK_parameters<-ggarrange(nTA_Sal, nDIC_Sal,
          #labels = c("DIC Friss regresion", "TA Friss regresion"),
          ncol = 2, nrow = 1)

FLK_parameters
```

**Figure 1:** Overview of linear regressions of total alkalinity (TA, µmol kg−1) and disolved inorganic carbon (DIC, µmol kg−1) as a function of salinity + Friss normalized values.

* Original data: Black line and circles
* Friis normalization: blue line and triangles
* Highest and lowest salinities are mostlikely wrong

## Bias of hour of the day per sample (EST)
 
```{r}
All_ToD<- ggplot(FLK.data) + 
  
  theme_bw() +
  scale_y_continuous(limits = c(0, 24),
                      expand = c(0.01, 0.01),
                      breaks = seq(0, 24, 2),
                      name="Time of the day")+
  
  theme(legend.position="bottom",
          plot.background=element_blank(),
          panel.grid = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )

```

```{r}
nTA_dat<-All_ToD +geom_point(aes(nTA, ToD, colour=Sub_region))#+
  #geom_smooth(aes(nDIC, ToD, colour=Sub_region), se=F)
ggMarginal(nTA_dat, groupColour = TRUE)

```

```{r}
nDIC_dat<-All_ToD +geom_point(aes(nDIC, ToD, colour=Sub_region))#+
  #geom_smooth(aes(nDIC, ToD, colour=Sub_region), se=F)
ggMarginal(nDIC_dat, groupColour = TRUE)

```

```{r}
omega_dat<-All_ToD +geom_point(aes(Aragonite_Sat_W, ToD, colour=Sub_region))#+
  #geom_smooth(aes(ToD, Aragonite_Sat_W, colour=Sub_region), se=F)
ggMarginal(omega_dat, groupColour = TRUE)
```

# 4. nTA and nDIC relation

## 4.1 Region (all FLK samples)

```{r}
nTA_nDIC<- ggplot(FLK.data, aes (nDIC, nTA)) + 
  
  scale_y_continuous(#limits = c(1700,2900),
                     #expand = c(0, 0),
                     #breaks = seq(1800, 2800, 100),
                    name="nTA") +
  scale_x_continuous(# limits = c(1600, 2600),
                     # expand = c(0, 0),
                     # breaks = seq(1500,2600,100),
                      name="nDIC")+
MyTheme

#TA_DIC+ 
 #geom_point(aes (fill=Region, shape=Season), alpha=0.5)+
 #scale_shape_manual(values=c(21, 22, 23, 24))

#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_sea<-nTA_nDIC +
   scale_shape_manual(values=c(21,21,24, 24))+
  geom_point(aes (fill=Season, shape=Zone), alpha=0.4)+
  geom_smooth(method = "lm", colour="black")
 
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_pre<-nTA_nDIC +
  scale_shape_manual(values=c(21,21,24, 24))+
  geom_point(aes (fill=Precipitation,  shape=Zone), alpha=0.4)+
  geom_smooth(method = "lm", colour="black")
 
```

```{r}
nTA_nDIC_parameters<-ggarrange(nTA_nDIC_sea, nTA_nDIC_pre,
          #labels = c("DIC Friss regresion", "TA Friss regresion"),
          ncol = 2, nrow = 1)

nTA_nDIC_parameters
```

**Figure 2:** Linear regressions of total alkalinity (nTA) as a function of disolved inorganic carbon (nDIC) for the Florida Keys .

Does this mean anything without offshore / inshore references?

```{r}
 # Individual LR for each region
    TA_DIC_lm <- FLK.data %>%
      group_by(Region) %>%
      do(mod = lm(nTA ~ nDIC, data = .))

    TA_DIC_coef <- FLK.data %>% 
                    group_by(Region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations", digits = 3)
```

## 4.2 By zone sub_region

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_sea_zone<-nTA_nDIC_sea + facet_grid(Zone~Sub_region)
nTA_nDIC_sea_zone
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_pre_zone<-nTA_nDIC_pre +  facet_grid(Zone~Sub_region)
nTA_nDIC_pre_zone
```

```{r}
 # Individual LR for each Zone and Sub_region
    TA_DIC_lm_zone <- FLK.data %>%
      group_by(Zone, Sub_region) %>%
      do(mod = lm(nTA ~ nDIC, data = .))

    TA_DIC_coef_zone <- FLK.data %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef_zone[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations", digits = 3)
```

**Notes: **

* Higher slopes in TA vs. DIC 
  * -> a higher NCC:NCP
  * -> calcifying (e.g., corals, sediments, and calcifying algae) relative to non-calcifying communities (e.g., fleshy algae)
  
* Intermediate slopes for mixed communities of calcifiers and non-calcifiers (Anthony et al., 2013; Page et al., 2016; Lantz et al., 2017). 


## 4.3 nTA nDIC outliers

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_Extreme<- ggplot() + 
    scale_y_continuous(#limits = c(1700,2900),
                     #expand = c(0, 0),
                     #breaks = seq(1800, 2800, 100),
                    name="nTA") +
  scale_x_continuous(# limits = c(1600, 2600),
                     # expand = c(0, 0),
                     # breaks = seq(1500,2600,100),
                      name="nDIC")+
  MyTheme +  facet_grid(Zone~Sub_region)+
  geom_point(data=FLK.data, aes (nDIC, nTA, fill=Extreme), shape=21, alpha=0.8)+
  geom_smooth(data=FLK.data[FLK.data$Extreme=="Normal", ], 
              aes (nDIC, nTA), method = "lm", colour="black")
nTA_nDIC_Extreme
```


```{r}
 # Individual LR for each Zone and Sub_region
    
    TA_DIC_coef_zone_noExtremes <- FLK.data[FLK.data$Extreme=="Normal", ] %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef_zone_noExtremes[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations without extreme events", digits = 3)
```

**Notes: **
* Offshore high nTA and nDIC during march 2012 cold mortality event - keep or remove?

# 5. Basic stats summary and visual

## 5.1 Temperature

```{r}
FLK.data$Date<-FLK.data$ESTDate
```

### Season stats 

```{r, echo=FALSE}
Temp.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Tmin = min (Temperature_C, na.rm = T), 
                Tmax = max (Temperature_C, na.rm = T),
                Tmean = mean (Temperature_C, na.rm = T), 
                Tsd = sd (Temperature_C, na.rm = T))

kable(as.data.frame(Temp.Season, format = "markdown"), caption = "Temperature by season")

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_All<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
Temperature_All +
  geom_point(aes (Date, Temperature_C, fill=Season), shape=21, alpha=0.8)

# Temperature_All +
#   geom_point(aes (Date, Temperature_C, fill=Extreme), shape=21, alpha=0.8) + facet_grid(Zone~.)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_month<- ggplot(FLK.data) +
  
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, Temperature_C, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
Temperature_month

```

## 5.2 Salinity 

### Season stats 

```{r, echo=FALSE}
Sal.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Sal_min = min (BestSalinity, na.rm = T), 
                Sal_max = max (BestSalinity, na.rm = T),
                Sal_mean = mean (BestSalinity, na.rm = T), 
                Sal_sd = sd (BestSalinity, na.rm = T))

kable(as.data.frame(Sal.Season, format = "markdown"), caption = "Salinity by season")

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_All<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(15,40),
                       #expand = c(0, 0),
                        name="Salinity",
                        breaks = seq(20, 40, 2)
                        ) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
Sal_All + 
  geom_point(aes (Date, BestSalinity, fill=Season), shape=21, alpha=0.8)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_All + 
  geom_point(aes (Date, BestSalinity, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 30, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 40, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_month<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(15,40),
                       #expand = c(0, 0),
                        name="Salinity",
                        breaks = seq(20, 40, 2)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, BestSalinity, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
Sal_month

```

### Salinity issues

```{r}
Salinity_low<-FLK.data[FLK.data$BestSalinity<30, ]
Salinity_high<-FLK.data[FLK.data$BestSalinity>40, ]
Salinity_Check<-rbind(Salinity_low, Salinity_high)
Salinity_Check<-Salinity_Check[!is.na(Salinity_Check$BestSalinity),]
Salinity_Check$Problem<-"salinity"
Salinity_Check
```

### Salinity - Temperatue correlations and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_Temp<- ggplot(FLK.data) + MyTheme+
  scale_x_continuous(limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 36, 2),
                       expand = c(0, 0)) +
  scale_y_continuous(name="Salinity",
                 #limits = c(0.5,6),
                 #expand = c(0, 0),
                 breaks = seq(1,40,2))+
  geom_abline(slope = 0, intercept = 30, color="red", linetype=2)+
  geom_abline(slope = 0, intercept = 39, color="red", linetype=2)+
  geom_vline(xintercept = 33, color="red", linetype=2)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_Temp +
  geom_point(aes (Temperature_C, BestSalinity, fill=Precipitation),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
  
Sal_Temp +  
  geom_point(aes (Temperature_C, BestSalinity, fill=factor(Extreme)),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
  
Sal_Temp +  
  geom_point(aes (Temperature_C, BestSalinity, fill=factor(Year)),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
```

## 5.3 Aragonite

### Season stats

```{r, echo=FALSE}
Aragonite.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Amin = min (Aragonite_Sat_W, na.rm = T), 
                Amax = max (Aragonite_Sat_W, na.rm = T),
                Amean = mean (Aragonite_Sat_W, na.rm = T), 
                Asd = sd (Aragonite_Sat_W, na.rm = T))

kable(as.data.frame(Aragonite.Season, format = "markdown"), caption = "Omega by season")
```

### Overview

```{r,echo=FALSE, fig.height=8, fig.width=8.8}
Aragonite_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("Aragonite Saturation") ,
                       breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="6 months")+
    MyTheme +
    geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

Aragonite_all + 
  geom_point(aes (Date, Aragonite_Sat_W, fill=Season), shape=21, alpha=0.8)

```

```{r, echo=FALSE, fig.height=8, fig.width=8.8}
Aragonite_all + 
  geom_point(aes (Date, Aragonite_Sat_W, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 4.5, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2.1, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Omega_month<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(15,40),
                       #expand = c(0, 0),
                        name="Aragonite Saturation",
                       breaks = seq(0, 5, 1),  
                       expand = c(0.02, 0.02)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, Aragonite_Sat_W, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
Omega_month
```

### Omega issues

```{r}
Omega_low<-FLK.data[FLK.data$Aragonite_Sat_W<2.1, ]
Omega_low2<-FLK.data[FLK.data$Aragonite_Sat_W<3 & FLK.data$Zone=="Oceanic", ]
Omega_high<-FLK.data[FLK.data$Extreme=="HighOmega_NoReason", ]
Omega_Check<-rbind(Omega_low, Omega_low2, Omega_high)
Omega_Check<-Omega_Check[!is.na(Omega_Check$Aragonite_Sat_W),]
Omega_Check$Problem<-"omega"
Omega_Check
```

###  Omega - Temperature correlation and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_Temp<- ggplot(FLK.data) +
    scale_x_continuous(limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 2),
                       expand = c(0, 0)) +
    scale_y_continuous(name="Omega",
                 limits = c(0.5,6),
                 expand = c(0, 0),
                 breaks = seq(1,6,1))+
  
  geom_smooth(aes(Temperature_C, Aragonite_Sat_W),
              linetype=2, method = "lm", color="black")+
  MyTheme
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_Temp +
  geom_point(aes (Temperature_C, Aragonite_Sat_W, fill=Precipitation),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
  
Arg_Temp +  
  geom_point(aes (Temperature_C, Aragonite_Sat_W, fill=factor(Extreme)),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
  
Arg_Temp +  
  geom_point(aes (Temperature_C, Aragonite_Sat_W, fill=factor(Year)),
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
```

### Omega - Salinity correlation and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_Sal<- ggplot(FLK.data) + 
  MyTheme +
  geom_smooth(aes(BestSalinity, Aragonite_Sat_W), 
              linetype=2, method = "lm", color="black")
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_Sal +
  geom_point(aes (BestSalinity, Aragonite_Sat_W, fill=Precipitation), alpha=0.5, shape=21) + facet_wrap(~Zone)

Arg_Sal +
  geom_point(aes (BestSalinity, Aragonite_Sat_W, fill=Extreme),
             alpha=0.5, shape=21)+ facet_wrap(~Zone)
Arg_Sal+
  geom_point(aes (BestSalinity, Aragonite_Sat_W, fill=factor(Year)), alpha=0.5, shape=21)+
  facet_wrap(~Zone)
```

## 5.4 TA

### Season stats 

```{r, echo=FALSE}
TA.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                TAmin = min (TA_umol_kg, na.rm = T), 
                TAmax = max (TA_umol_kg, na.rm = T),
                TAmean = mean (TA_umol_kg, na.rm = T), 
                TAsd = sd (TA_umol_kg, na.rm = T))

kable(as.data.frame(TA.Season, format = "markdown"), caption = "TA by season")

nTA.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                TAmin = min (nTA, na.rm = T), 
                TAmax = max (nTA, na.rm = T),
                TAmean = mean (nTA, na.rm = T), 
                TAsd = sd (nTA, na.rm = T))

kable(as.data.frame(nTA.Season, format = "markdown"), caption = "nTA by season")
```

### Overview - outliers

```{r, echo=FALSE, fig.height=8.0, fig.width=8.8}
nTA_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("nTA") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
    #geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

nTA_all + 
  geom_point(aes (Date, nTA, fill=Season), shape=21, alpha=0.8)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_all + 
  geom_point(aes (Date, nTA, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 2400, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 2300, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2500, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_month<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nTA") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.02, 0.02)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, nTA, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
nTA_month
```

### nTA issues

```{r}
TA_low<-FLK.data[FLK.data$nTA<2000, ] # One sample (WS20231_26) low TA no DIC
TA_high<-FLK.data[FLK.data$nTA>2780, ] # One sample (WS17030_16) high
TA_Check<-rbind(TA_low, TA_high)
TA_Check<-TA_Check[!is.na(TA_Check$nTA),]
TA_Check$Problem<-"TA"
TA_Check
```

### Omega- nTA scatterplot and outliers

```{r,  echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_nTA<- ggplot(FLK.data) + MyTheme+
  annotate(geom = "rect", alpha = .2,
           xmin = 2300, xmax = 2450, ymin = 4.6, ymax = 5.1 )+
  
  geom_smooth(aes(nTA, Aragonite_Sat_W), linetype=2, 
              method = "lm", color="black")
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_nTA + 
  geom_point(aes (nTA, Aragonite_Sat_W, fill=Precipitation), 
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)

Arg_nTA +  
  geom_point(aes (nTA, Aragonite_Sat_W, fill=factor(Year)), 
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)

Arg_nTA +  
  geom_point(aes (nTA, Aragonite_Sat_W, fill=factor(Extreme)), 
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)
```

## 5.5 DIC

### Season stats 

```{r, echo=FALSE}
DIC.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                DIC_min = min (DIC_umol_kg, na.rm = T), 
                DIC_max = max (DIC_umol_kg, na.rm = T),
                DIC_mean = mean (DIC_umol_kg, na.rm = T), 
                DIC_sd = sd (DIC_umol_kg, na.rm = T))
kable(as.data.frame(DIC.Season, format = "markdown"), caption = "DIC by season")

nDIC.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                nDIC_min = min (nDIC, na.rm = T), 
                nDIC_max = max (nDIC, na.rm = T),
                nDIC_mean = mean (nDIC, na.rm = T), 
                nDIC_sd = sd (nDIC, na.rm = T))
kable(as.data.frame(nDIC.Season, format = "markdown"), caption = "nDIC by season")
```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
nDIC_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("nDIC") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
    #geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

nDIC_all + 
  geom_point(aes (Date, nDIC, fill=Season), shape=21, alpha=0.8)

```

```{r,  echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_all + 
  geom_point(aes (Date, nDIC, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 2200, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2000, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_month<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nDIC") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.02, 0.02)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, nTA, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
nDIC_month
```

### nDIC issues

Not filtering additional data becuase of nDIC

### Omega - nDIC scatterplot and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_nDIC<- ggplot(FLK.data) + 
  geom_smooth(aes(nDIC, Aragonite_Sat_W), linetype=2, 
              method = "lm", color="black")+
  MyTheme
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}

Arg_nDIC +
    geom_point(aes (nDIC, Aragonite_Sat_W, fill=Precipitation), alpha=0.5, shape=21)+
    facet_wrap(~Zone)
  
Arg_nDIC +  
  geom_point(aes (nDIC, Aragonite_Sat_W, fill=Extreme), alpha=0.5, shape=21)+
  facet_wrap(~Zone)

```

**NOTE:** Review Omega calculations for 2011 -  Very high values for normal DIC and TA -  including offshore and ocean samples


## 5.6 pH

### Season stats 

```{r, echo=FALSE}
head(FLK.data)
pH.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                pH_min = min (pH_calculated, na.rm = T), 
                pH_max = max (pH_calculated, na.rm = T),
                pH_mean = mean (pH_calculated, na.rm = T), 
                pH_sd = sd (pH_calculated, na.rm = T))
kable(as.data.frame(pH.Season, format = "markdown"), caption = "pH by season")

```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
pH_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("pH calculated") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
    #geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

pH_all + 
  geom_point(aes (Date, pH_calculated, fill=Season), shape=21, alpha=0.8)

```

```{r,  echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_all + 
  geom_point(aes (Date, pH_calculated, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 2200, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2000, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_month<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pH calculated") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.02, 0.02)) +
  scale_x_continuous(name="Month",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks =seq(0,12,2))+
  
  geom_point(aes (MoY, pH_calculated, fill=Extreme), shape=21, alpha=0.8)+
  MyTheme +  facet_grid(Zone~Sub_region)
pH_month
```

### pH issues
```{r}
pH_low<-FLK.data[FLK.data$pH_calculated<7.95 & FLK.data$Zone=="Oceanic", ]
pH_low$Problem<-"pH(low_for_ocean)"
```


### Omega - nDIC scatterplot and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_pH<- ggplot(FLK.data) + 
  geom_smooth(aes(pH_calculated, Aragonite_Sat_W), linetype=2, 
              method = "lm", color="black")+
  MyTheme
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Arg_pH +
    geom_point(aes (pH_calculated, Aragonite_Sat_W, fill=Precipitation),
               alpha=0.5, shape=21)+
    facet_wrap(~Zone)
  
Arg_pH +  
  geom_point(aes (pH_calculated, Aragonite_Sat_W, fill=Extreme), 
             alpha=0.5, shape=21)+
  facet_wrap(~Zone)

```

**NOTE:** Review Omega calculations for August 2011 -  Very high values for normal DIC and TA -  including offshore and ocean samples

# 6 Remove outliers

```{r}
Remove<-rbind(Salinity_Check, Omega_Check, TA_Check, pH_low)
Remove <-Remove %>% 
        filter(!duplicated(CTDID))

#write.csv(Remove, "FLK_results/ValuesToRemove_V4.csv", row.names = F)

FLK.data_filtered<-FLK.data[!(FLK.data$CTDID %in% Remove$CTDID),]
FLK.data_filtered<-FLK.data_filtered%>% select (- (ncrmp_flag: seacarb_id))
#str(FLK.data_filtered)
#write.csv(FLK.data_filtered, "FLK_results/FLK_filtered_ve4.csv", row.names = F)
```

```{r}

```

# 7. Notes/ideas

* Regional CC -> offshore data
* Local carbonate chemistry: 
  * Seasonal (light), storms, upwelling, salinity (rain). 
  * Biological: coral/seagrass/macroalgae cover 
  * Biological + Seasonal: Photosyntesis, respiration.
  * Physical: inlets, rivers, upwelling

## Manzello (2012)

* local carbonate chemistry: Variation on CO2, alkalinity, and salinity - Florida Reef Tract (FRT) data.

* Meassure total CO2 (TCO2) - coulometrically and total alkalinity (TA) - gran titration. Other paramethers derived 
* Predominantly in inshore / upper FRT (higher than modeled). 
* H Productivity -> net uptake of total CO2 (TCO2) -> H aragonite
*Offshore reefs: oceanic carbonate chemistries consistent with present day tropical surface ocean conditions.
* Photosynthetic uptake of TCO2 by seagrasses/macroalgae in the inshore waters of the FRT. Acidification refugia (spatial * time)

## Uthicke (2014)

* GBR - 14 Inshore fringing  reefs
Meassured: TA and DIC. Derived:pCO2, pH and aragonite
* TA: 2069 - 2364 mmol kg2
* DIC:1846 - 2099 mmol kg2
* pCO2: 340 - 554 matm
  * Higher wet seasons
  * Inshore reefs above atmospheric values.
  * Arg was not further reduced in the wet season (temp effects)
  *Thermodynamic effects and anthropogenic runoff (P, R and P/R ratios).
  * Expected slope of  linear regression bw DIC and TA in systems where calcification is dominating is ~ 2.0 
  
## Cyronak (2018)

* Net community production; NCP - organic
* net community calcification; NCC inorganic
* 23 coral reef locations across the globe - derived from TA and DIC
* All reefs were net calcifying for the majority of observations (alkalinity depletion relative to offshore)
* Occasional observations of net dissolution occurred at most locations
* Influence of organic carbon fluxes on total changes in dissolved inorganic carbon (DIC) (i.e., NCP compared to the sum of NCP and NCC) =  32% to 88% -> biogeochemical differences between reefs. 
* Reefs with the largest relative percentage of NCP experienced the largest variability in seawater pH for a given change in DIC -> ability to elevate or suppress local pH relative to the open ocean.

## Ian (2019) 

* Reefs and inlets were sampled
* Reefs: Elevated pCO2 in warmer wet season
* Inlets: more dynamic -> periodic pulses of acidified water -> more acidification than reefs. 
  - Negative correlation bw salinity and both TA, and DIC. Elevated TA and DIC in low salinity waters ->  carbonate dissolution as a result of organic matter decomposition?.