---
title: "LongTrends_bouy - "
author: "Ana Palacio-Castro"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 8
    df_print: paged
    toc: yes
    toc_float: true
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, options(knitr.kable.NA = ''))
```

# Libraries and settings

```{r, include=FALSE}
# Libraries
    library(plyr)
    library(tidyverse)
    library(reshape2)
    library(lubridate)
    library(knitr)
    library(dplyr)
    library(broom)

    library(ggpubr)
    library(ggthemes)
    library(gridExtra)
    library(ggExtra)
    
#Models     
    library(lmerTest)
    library(emmeans)

# Interactive Maps
    library(leaflet)

# Plots
MyTheme<-theme_bw() +  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )

```

# 1. Import and format carbon chemistry data

```{r, include=FALSE}
# 1. Get data
Bouy.data<-read.csv("Data/MAPCO2ALL.csv", header = T)
str(Bouy.data)
#Bouy.data$Region<-NULL


# 2. Format variables
  # Date/times
   
  # UTC Date
    Bouy.data <- Bouy.data %>% mutate(Date_Time = mdy_hms(Date_Time)) 
    Bouy.data <- Bouy.data %>% mutate(
                    Date = date(Date_Time), 
                    Year = year(Date_Time), 
                    month = month(Date_Time), 
                    #Day = day(Date_Time),
                    hour = hour(Date_Time)
                    #minute = minute(Date_Time),
                    #second = second(Date_Time)
                    )
    str(Bouy.data)
    
    Bouy.data$Month<- month.abb[Bouy.data$month]
    Bouy.data$Month<-factor(Bouy.data$Month, 
                          levels = c("Jan", "Feb", "Mar",
                                     "Apr", "May","Jun",
                                    "Jul", "Aug", "Sep",
                                    "Oct","Nov","Dec"
                                    ))
    
    
# # Define seasons (rougly by month)
 metseasons <- c(
    "01" = "Winter", "02" = "Winter", "03" = "Winter",
    "04" = "Spring", "05" = "Spring", "06" = "Spring",
    "07" = "Summer", "08" = "Summer", "09" = "Summer",
    "10" = "Fall", "11" = "Fall", "12" = "Fall"
  )
Seasons<-as.data.frame(metseasons[format(Bouy.data$Date, "%m")])
colnames(Seasons)<-"Season"
Bouy.data<-cbind(Bouy.data, Seasons)
      
Bouy.data$Season<-factor(Bouy.data$Season, levels = c(
                       "Winter", "Spring", 
                       "Summer", "Fall"))

summary(Bouy.data)

```




## 2 Number of samples

### By zone and location

```{r, echo=FALSE}
Cases_Year_Month<-Bouy.data %>% count(Year, Month,
                                  sort = F)

Cases_Year_Month<-as.data.frame(Cases_Year_Month %>%
                   pivot_wider(names_from = Year,
                   values_from = n))
# Organize table
 #Cases_Year_Month<-Cases_Year_Month %>% 
 #   select(sort(names(.)))

kable(as.data.frame(Cases_Year_Month, format = "html"), caption="Samples collected by year-month")
#write.csv(Cases_Year_Month, "FLK_results/SampleS_Month_Year.csv")
```

# 5. Basic plots and stats summary - Seasonality

## 5.1 Temperature

### Season stats 

```{r, echo=FALSE}
Temp.Season <- ddply (Bouy.data, .(Season),summarise,
                Tmin = min (Temperature_C, na.rm = T), 
                Tmax = max (Temperature_C, na.rm = T),
                Tmean = mean (Temperature_C, na.rm = T), 
                Tsd = sd (Temperature_C, na.rm = T))

kable(as.data.frame(Temp.Season, format = "markdown"),
      caption = "Temperature by season", digits = 2)

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_All<- ggplot(Bouy.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
Temperature_All +
  geom_point(aes (Date, Temperature_C, fill=Season), shape=21, alpha=0.8)

# Temperature_All +
#   geom_point(aes (Date, Temperature_C, fill=Extreme), shape=21, alpha=0.8) + facet_grid(Zone~.)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_month<- ggplot(Bouy.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 4),  
                       expand = c(0.1, 0.1)) +
  MyTheme+
    geom_boxplot(data=Bouy.data, 
                 aes (x=Month, y=Temperature_C))+
    scale_shape_manual(values=c(24, 25, 21))+
    geom_point(data=Bouy.data, aes (x=Month, y=Temperature_C, fill=Season), 
             alpha=0.8, size=1, shape=21)
Temperature_month

```

# **Figure S1:** Seasonality_temperature

## 5.2 Salinity 

### Season stats 

```{r, echo=FALSE}
Sal.Season <- ddply (Bouy.data, .(Season),summarise,
                Sal_min = min (Salinity_CTD, na.rm = T), 
                Sal_max = max (Salinity_CTD, na.rm = T),
                Sal_mean = mean (Salinity_CTD, na.rm = T), 
                Sal_sd = sd (Salinity_CTD, na.rm = T))

kable(as.data.frame(Sal.Season, format = "markdown"), caption = "Salinity by season")

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
SAl_All<- ggplot(Bouy.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Salinity")),
                       breaks = seq(15, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
SAl_All +
  geom_point(aes (Date, Salinity_CTD, fill=Season), shape=21, alpha=0.8)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_month<- ggplot(Bouy.data) + 
   scale_y_continuous(#limits = c(15,40),
                       #expand = c(0, 0),
                        name="Salinity",
                        breaks = seq(20, 40, 2)
                        ) +
  MyTheme +
    geom_boxplot(aes (x=Month, y=Salinity_CTD))+
    geom_point(data=Bouy.data, aes (x=Month, y=Salinity_CTD, 
                                 fill=Season), shape=21, 
             alpha=0.8, size=1)
Sal_month
```

### Salinity - Temperature correlations and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_Temp<- ggplot(Bouy.data) + MyTheme+
  scale_x_continuous(limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 36, 2),
                       expand = c(0, 0)) +
  scale_y_continuous(name="Salinity",
                 #limits = c(0.5,6),
                 #expand = c(0, 0),
                 breaks = seq(1,40,2))+
  geom_abline(slope = 0, intercept = 30, color="red", linetype=2)+
  geom_abline(slope = 0, intercept = 39, color="red", linetype=2)+
  geom_vline(xintercept = 33, color="red", linetype=2)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_Temp +
  geom_point(aes (Temperature_C, Salinity_CTD),
             alpha=0.5, shape=21)
```

## 5.6 pCO2 

### Season stats 

```{r, echo=FALSE}
pCO2.Season <- ddply (Bouy.data, .(Season),summarise,
                pH_min = min (pCO2_uatm, na.rm = T), 
                pCO2_uatm_max = max (pCO2_uatm, na.rm = T),
                pCO2_uatm_mean = mean (pCO2_uatm, na.rm = T), 
                pCO2_uatm_sd = sd (pCO2_uatm, na.rm = T))
kable(as.data.frame(pCO2.Season, format = "markdown"), caption = "pCO2 by season")
```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
pCO2_all<- ggplot(Bouy.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    geom_point(aes (Date, pCO2_uatm, fill=Season), shape=21, alpha=0.8)+
    MyTheme
pCO2_all  

pCO2_all + facet_wrap(~Season)
 

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_month<- ggplot(Bouy.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("pCO2")),
                       breaks = seq(200, 600, 100),
                       expand = c(0.03, 0.03)
                        ) +
  MyTheme 

pCO2_month +
  geom_boxplot(aes (x=Month, y=pCO2_uatm))+
  geom_point(aes (x=Month, y=pCO2_uatm, fill=Season), 
             shape=21, size = 1, alpha=0.8)+
  facet_wrap(~Year)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_month +
  geom_boxplot(data=Bouy.data[Bouy.data$Extreme=="Normal", ], 
               aes (x=Month, y=pCO2_uatm))+
  geom_point(aes (x=Month, y=pCO2_uatm), 
             shape=21, size = 1, alpha=0.5)
```

## 5.7 pH 

### Season stats 

```{r, echo=FALSE}
pH.Season <- ddply (Bouy.data, .(Season),summarise,
                pH_min = min (pH_measured, na.rm = T), 
                pCO2_uatm_max = max (pH_measured, na.rm = T),
                pCO2_uatm_mean = mean (pH_measured, na.rm = T), 
                pCO2_uatm_sd = sd (pH_measured, na.rm = T))
kable(as.data.frame(pH.Season, format = "markdown"), caption = "pH  (calculated) by season")

```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
pH_all<- ggplot(Bouy.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("pH") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
  
pH_all + 
  geom_point(aes (Date, pH_measured, fill=Season), shape=21, alpha=0.8)

```

```{r.  echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_all + 
  geom_point(aes (Date, pH_measured, fill=Season), shape=21, alpha=0.8)+
  #geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 7.95, color="red", linetype=1)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_month<- ggplot(Bouy.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("pH")),
                       breaks = seq(0, 9, 0.1),
                       expand = c(0.03, 0.03)
                        ) +
  MyTheme+
  geom_boxplot(aes (x=Month, y=pH_measured))+
  geom_point(aes (x=Month, y=pH_measured, fill=Season), 
             shape=21, size = 1, alpha=0.8)
pH_month
```

**Notes from Dereks' paper: **

* January 2010: High inshore TCO2 and TA in the UK after the cold-water mass mortality of reef-building corals that occurred at inshore patch reefs 
* August 2010: persistent winds at 5 to 7.5 m s21 and overcast skies during sampling. -> lower than normal nTA -> spike in pCO2 and depression in arag at both sites, erasing any inshore-to-offshore gradient for these two parameters
* October 2011:  high rainfall -> low salinity at all sites, with salinities inshore and offshore ranging from 32.04– 32.685 and 34.035–34.835, respectively. At the inshore sites, low salinity was coincident with a spike in pCO2 and depression in arag. All sites showed net respiration during this time

# 8. Long Term trends in FLK (Al zones) using linear models

This approach is not optimum because of strong seasonality. Especially in the reef. However it is useful to compare the long term predictions with the ones from gam models. 

To deal with seasonality, include Season in the model. Month gets noisy since some month have been sampled very few times

## 8.5 pCO2 - all data

```{r}
pCO2_all<- ggplot(Bouy.data,
                          aes(x=Date, y=pCO2_uatm)) +
  
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="2 year")+

  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5, size=1)
pCO2_all

```

## 8.6 pH - - all data

```{r}
pH_all<- ggplot(Bouy.data,
                          aes(x=Date, y=pH_measured)) +
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pH") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="2 year")+

  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5, size=1)
pH_all
```


# 9 pCO2 LMERs

## 9.1 pCO2 - Cheeka

### Raw data

```{r}
pCO2_data_o<- ggplot(Bouy.data,
                          aes(x=Date, y=pCO2_uatm)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2 -Cheeka") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+
  
  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Month)), shape=21, alpha=0.5)
pCO2_data_o
```

### Model

```{r}
pCO2_mod<-lmer(pCO2_uatm~Year * Season +
                                 (1|Month), 
                                 data=Bouy.data)
# Subregion and zone are not significant

summary(pCO2_mod)    
anova(pCO2_mod)
ranova(pCO2_mod)
#step(pCO2_mod)

par(mfrow=c(2,3))
plot(pCO2_mod)
acf(resid(pCO2_mod), main="acf(resid(pCO2 Cheeka))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(Month=unique(Bouy.data$Month) ,
                      Season=unique(Bouy.data$Season) ,
                      Year=seq(min(Bouy.data$Year), 
                               max(Bouy.data$Year), by=1) )
  
  pCO2_Pred <- predict(pCO2_mod, newdata=NewData, 
                       re.form=NA, level=0, asList = FALSE)
  
  pCO2_Pred <-cbind(NewData, pCO2_Pred)
  pCO2_Pred$Date<-as.Date(as.character(pCO2_Pred$Year), format = "%Y")
  
  
# Plot raw data point and fitted model 
  
  pCO2_Modeled<-ggplot(Bouy.data) + MyTheme+
     scale_y_continuous(#limits = c(0,6),
                       name=expression(paste(pCO[2], ~" (", mu, " atm)")),
                       #limits = c(2.3, 5.2),
                       #breaks = seq(0, 10, 0.5),  
                       expand = c(0.02, 0.02)) +
    
      geom_point(data=Bouy.data, 
                               aes(y=pCO2_uatm, x=Date, 
                                  #fill = Season), 
                                  colour = Season), 
                               alpha=0.5, size=0.5, shape=21)+
      geom_line(data=pCO2_Pred, aes(y = pCO2_Pred,
                                    x=Date, colour = Season),
                linetype=1, size=1) 
  pCO2_Modeled
```

## 9.2 pH - Cheeka

### Raw data

```{r}
pH_plot<- ggplot(Bouy.data,
                          aes(x=Date, y=pH_measured)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pH -Cheeka") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+
  
  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Month)), shape=21, alpha=0.5)
pH_plot
```

### Model

```{r}
pH_mod<-lmer(pH_measured~Year * Season +
                                 (1|Month), 
                                 data=Bouy.data)
# Subregion and zone are not significant

summary(pH_mod)    
anova(pH_mod)
ranova(pH_mod)
#step(pCO2_mod)

par(mfrow=c(2,3))
plot(pH_mod)
acf(resid(pH_mod), main="acf(resid(pCO2 Cheeka))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(Month=unique(Bouy.data$Month) ,
                      Season=unique(Bouy.data$Season) ,
                      Year=seq(min(Bouy.data$Year), 
                               max(Bouy.data$Year), by=1) )
  
  pH_Pred <- predict(pH_mod, newdata=NewData, 
                       re.form=NA, level=0, asList = FALSE)
  
  pH_Pred <-cbind(NewData, pH_Pred)
  pH_Pred$Date<-as.Date(as.character(pH_Pred$Year), format = "%Y")
  
  
# Plot raw data point and fitted model 
  
  pH_Modeled<-ggplot(Bouy.data) + MyTheme+
     scale_y_continuous(#limits = c(0,6),
                       #name=(expression(~Omega[Ar])),
                       #limits = c(2.3, 5.2),
                       #breaks = seq(0, 10, 0.5),  
                       expand = c(0.02, 0.02)) +
    
      geom_point(data=Bouy.data, 
                               aes(y=pH_measured, x=Date, 
                                  #fill = Season), 
                                  colour = Season), 
                               alpha=0.5, size=0.5, shape=21)+
      geom_line(data=pH_Pred, aes(y = pH_Pred,
                                    x=Date, colour = Season),
                linetype=2, size=1) 
  pH_Modeled
```
