---
title: "Carbon Chemistry analysis - New database-Filtered"
author: "Ana Palacio-Castro"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    fig_height: 8
    fig_width: 8
    df_print: paged
    toc: yes
    toc_float: true
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, options(knitr.kable.NA = ''))
```

# Libraries and settings

```{r, include=FALSE}
# Libraries
    library(plyr)
    library(tidyverse)
    library(reshape2)
    library(lubridate)
    library(knitr)
    library(dplyr)
    library(broom)

    library(ggpubr)
    library(ggthemes)
    library(gridExtra)
    library(ggExtra)
    
#Models     
    library(lmerTest)
    library(emmeans)

# Interactive Maps
    library(leaflet)

# Plots
MyTheme<-theme_bw() +  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )

```

# 1. Import and format carbon chemistry data

```{r, include=FALSE}
# 1. Get data
FLK.data<-read.csv("FLK_results/FLK_filtered.csv", header = T)
#FLK.data$Region<-NULL
FLK.data$Mission<-NULL
FLK.data$Location<-NULL
FLK.data$Sample_Depth_m<-NULL

FLK.data$TA_0<-NULL
FLK.data$DIC_0<-NULL
FLK.data$nTA<-NULL
FLK.data$nDIC<-NULL

  #summary(FLK.data)
  str(FLK.data)
  Sites<-as.data.frame(unique(FLK.data$SiteID))
  
# 2. Format variables
  # Date/times
    # Year
    FLK.data$Year<-as.numeric(FLK.data$Year)
    summary(FLK.data$Year)
    
    # UTC Date
    #FLK.data$UTCDate<-as.Date(FLK.data$UTCDate, "%m/%d/%Y", tz="UTC")
    #summary(FLK.data$UTCDate)
  
    # UTC Date-time 
    #FLK.data$UTCDate_Time<-paste(FLK.data$UTCDate, FLK.data$UTCTime, sep = " ")
    #FLK.data$UTCDate_Time<-as_datetime(FLK.data$UTCDate_Time, tz="UTC")
    #summary(FLK.data$UTCDate_Time)
    
    # EST Date-time 
    #FLK.data$datetime<-as_datetime(FLK.data$UTCDate_Time, tz="EST")
    #FLK.data$ESTDate<-as.Date(FLK.data$datetime, tz="EST")
    #FLK.data$ESTTime <- format(FLK.data$datetime,"%H:%M:%S")
   
    #CC.data$Month<-month(CC.data$ESTDate)
    #FLK.data$Month <- as.numeric(format(FLK.data$ESTDate,"%m"))
    #summary(FLK.data$Month)
    #FLK.data$Month<-month.abb[FLK.data$Month]
    #CC.data$Month<-factor(CC.data$Month, levels = month.name)
    FLK.data$Month<-factor(FLK.data$Month, 
                          levels = c("Apr", "May","Jun",
                                    "Jul", "Aug", "Sep",
                                    "Oct","Nov","Dec",
                                    "Jan", "Feb", "Mar"))
    summary(FLK.data$Month)
    #FLK.data$Months<-months(FLK.data$ESTDate)
    FLK.data$Months<-factor(FLK.data$Months, levels = month.name)
    FLK.data$Date<-as.Date(FLK.data$Date)
    
  ## Add time variables 

    # FLK.data <- transform(FLK.data,
    #                    SiteID = factor(SiteID),
    #                    MY = format(datetime, format = '%Y-%m'),
    #                    MoY = as.numeric(format(datetime, format = '%m')),
    #                    #DoY = as.numeric(format(datetime, format = '%j')),
    #                    ToD = as.numeric(format(datetime, format = '%H')) +
    #                      (as.numeric(format(datetime, format = '%M')) / 60))
    
  FLK.data$Sub_region<-factor(FLK.data$Sub_region, levels = c(
                          "Biscayne", "UK", "MK", "LK"))
  
  FLK.data$Zone<-factor(FLK.data$Zone, levels = c(
                        "Inshore", "Mid channel", 
                        "Offshore", "Oceanic"))
    FLK.data$Season<-factor(FLK.data$Season, levels = c(
                        "Winter", "Spring", 
                        "Summer", "Fall"))

summary(FLK.data)

   # Numerical data
    # CC.data$Latitude <-as.numeric((as.character(CC.data$Latitude)))
    # CC.data$Longitude <-as.numeric((as.character(CC.data$Longitude)))
   
    # CC.data$Temperature_C <-
    #    as.numeric((as.character(CC.data$Temperature_C)))
    # Temperature_NA2<-CC.data[(is.na(CC.data$Temperature_C)),]
  
    # CC.data$TA <-as.numeric((as.character(CC.data$TA)))
    # CC.data$DIC <-as.numeric((as.character(CC.data$DIC)))
    
    # CC.data$pH <-as.numeric((as.character(CC.data$pH)))
    # CC.data$pCO2 <-as.numeric((as.character(CC.data$pCO2)))
    # CC.data$Aragonite_Sat_W<-
    #   as.numeric((as.character(CC.data$Aragonite_Sat_W)))
```

## Seasonality

* Winter: Dec 20-March 19
* Spring: March 20-June 18
* Summer: June 19-Sep 20 
* Fall: Sep 21-Dec 19

* Wet: May - October
* Dry: November - April


## Remove extreme events?

```{r}
# Label and filter extreme events
  FLK.data$Extreme<-as.factor(FLK.data$Extreme)
  summary(FLK.data$Extreme)
```

# 2. Check data available

## 2.1 Locations (all samples)

```{r MapINformation, include=FALSE}
Locations <- FLK.data %>% select(Latitude,
                                Longitude, 
                                Sub_region, 
                                SiteID)
Locations$GPS<-paste(Locations$Latitude,
                     "-", 
                     Locations$Longitude)

Locations<-unique(Locations)

GPS.Sites <- ddply (FLK.data, .(Sub_region, SiteID),summarise,
                Lat = mean (Latitude, na.rm = F), 
                Lon = mean (Longitude, na.rm = F),
                number = n())
#write.csv(GPS.Sites, "FLK_results/meanSitePoints.csv")

  #stations$Site<-as.factor(stations$Site)
  #pal.gen <- colorFactor(palette = "Set1",
  #                       domain = Locations$Location)
  pal.gen <- colorFactor(palette = "Set1",
                         domain = FLK.data$Zone)
```


```{r makeAmap, echo=FALSE}

leaflet(FLK.data, height = '400px') %>% 
  addTiles() %>%
  #addProviderTiles(providers$Esri.WorldImagery)%>%
  addProviderTiles(providers$OpenStreetMap) %>% 
  #addMarkers(icon=coral.icon) %>% 
  addCircleMarkers(lng = ~Longitude, lat = ~Latitude, 
                   #stroke = TRUE, 
                   radius = sqrt(GPS.Sites$number), 
                   fillOpacity = 1,
                   color = ~pal.gen(Zone),
                   label = ~SiteID,
                   labelOptions = labelOptions(
                     noHide = F, direction = "bottom",
                     textOnly = TRUE,
                     style = list(
        "color" = "white")))  %>%
  addLegend(position = "topright",
            pal = pal.gen, 
            values = ~Zone, opacity = 1) %>%
  fitBounds(lng1=-81.20, lat=26, lng2=-80.5, lat2=24)
  
```

**Figure:** Map of the sites where individual samples were collected

**Notes:**
* Check location of individual SiteIDs

## 2.2 Average GPS point location

```{r WS.Map, include=FALSE}
# Map information

WS.GPS.Sites <- ddply (FLK.data, .(Sub_region, Zone, SiteID),summarise,
                Lat = mean (Latitude, na.rm = F), 
                Lon = mean (Longitude, na.rm = F),
                number = n())

#Change color depending on type of data?
  #stations$Site<-as.numeric(stations$Site)
  # pal <- colorNumeric(palette = "YlOrRd", 
                      #domain = stations$Site)
  
  #stations$Site<-as.factor(stations$Site)
  #pal.gen <- colorFactor(palette = "Set1",
  #                       domain = Locations$Location)
  pal.gen <- colorFactor(palette = "Set1",
                         domain = WS.GPS.Sites$Zone)
```


```{r WSmap, echo=FALSE}

leaflet(WS.GPS.Sites, height = '600px') %>% 
  addTiles() %>%
  #addProviderTiles(providers$Esri.WorldImagery)%>%
  addProviderTiles(providers$OpenStreetMap) %>% 
  addCircleMarkers(lng = ~Lon, lat = ~Lat, 
                   stroke = FALSE, 
                   radius = 4, 
                   fillOpacity = 1,
                   color = ~pal.gen(Zone),
                   label = ~SiteID,
                   labelOptions = labelOptions(
                     noHide = F, direction = "bottom",
                     textOnly = TRUE,
                     style = list(
        "color" = "white")))  %>%
  addLegend(position = "topright",
            pal = pal.gen, 
            values = ~Zone, opacity = 1) %>%
  fitBounds(lng1=-81.20, lat=26, lng2=-80.5, lat2=24)
  
```

**Figure:** Permanent location of WS stations

## 2.3 Number of samples

### By zone and location

```{r, echo=FALSE}
Cases_Loc_Zone<-FLK.data %>% count(Sub_region,
                                  Zone,
                                  sort = F)

Cases_Loc_Zone<-as.data.frame(Cases_Loc_Zone %>%
                   pivot_wider(names_from = Zone,
                   values_from = n))
#write.csv(Cases_Loc_Zone, "FLK_results/SampleSizeFLK.csv")

kable(as.data.frame(Cases_Loc_Zone, format = "markdown"), 
      longtable = TRUE)
```

### By year and sub_region

```{r, echo=FALSE}
Cases_Reg_Year<-FLK.data %>% count(Year, Sub_region, sort = F)

Cases_Reg_Year<-as.data.frame(Cases_Reg_Year %>%
    pivot_wider(names_from = Year, values_from = n))
#write.csv(Cases_Reg_Year, "FLK_results/SampleYearFLK.csv")

kable(as.data.frame(Cases_Reg_Year, format = "html"),  caption = "Samples collected in each year")
```

### By climatological season and region

```{r, echo=FALSE}
Cases_Reg_season<-FLK.data %>% count(Season, Sub_region, sort = T)

Cases_Reg_season<-as.data.frame(Cases_Reg_season %>%
    pivot_wider(names_from = Season, values_from = n))
#write.csv(Cases_Reg_season, "FLK_results/SampleSeasonFLK.csv")

kable(as.data.frame(Cases_Reg_season, format = "html"),
      caption = "Samples collected in each season")
```

### By Month-year

```{r, echo=FALSE}

Cases_Month<-FLK.data %>% count(Year,
                                Month, sort = F)

Cases_Month<-as.data.frame(Cases_Month %>%
    pivot_wider(names_from = Year, values_from = n))

# Organize table
  #Cases_Month<-Cases_Month %>% 
  #    select(sort(names(.)))
#write.csv(Cases_Month, "FLK_results/SampleMonthYearFLK.csv")

kable(as.data.frame(Cases_Month, format = "html"), caption="Samples collected by year-month")
#write.csv(Cases_Mission, "WS_samples.csv")
```

### By Month-region

```{r, echo=FALSE}

Cases_Month_Location<-FLK.data %>% count(Sub_region,
                                Zone,
                                Month, sort = F)

Cases_Month_Location<-as.data.frame(Cases_Month_Location %>%
    pivot_wider(names_from = Month, values_from = n))
#write.csv(Cases_Month_Location, "FLK_results/SampleMonthZoneFLK.csv")

kable(as.data.frame(Cases_Month_Location, format = "html"),
      caption="Samples collected by month-Location")
```

### Per station during all sampling time

```{r, echo=FALSE}
Cases_Site_FLK<-FLK.data %>% count(Year, SiteID, sort = F)
#Cases_Site_FLK

Cases_Site_FLK<-as.data.frame(Cases_Site_FLK %>%
    pivot_wider(names_from = Year, values_from = n))
#write.csv(Cases_Site_FLK, "FLK_results/SampleSiteIDFLK.csv")

kable(as.data.frame(Cases_Site_FLK, format = "html"),
      caption = "Samples collected in SiteIDs")
```

**Notes:** 

* 


# 3. TA and DIC salinity normalization

## Salinity standardizations 

1. Used salinity Bottle first, if not available, salinity CTD

2. Calculate TA intercepts

```{r}
    
    # Individual LR for each region
    TA_lm <- FLK.data %>%
      group_by(Region) %>%
      do(mod = lm(TA_umol_kg ~ BestSalinity,data = .))

    TA_coef <- FLK.data %>% 
                group_by(Region) %>%
                do({model = lm(TA_umol_kg~BestSalinity, data=.)  # model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info
    
```

3. Calculate DIC intercepts 

```{r}
# 3.DIC normalization to intercept  

    DIC_coef <- FLK.data %>% 
                  group_by(Region) %>%
                  do({model = lm(DIC_umol_kg~BestSalinity, data=.)  
                  # create model
                  data.frame(tidy(model), # get coefficient info
                  glance(model))})        # get model info
```

4. Normalize with Friss equation

```{r}
# 4. Normalize the data

  TA_TO<-subset(TA_coef, term=="(Intercept)")
  TA_TO<-as.data.frame(select(TA_TO, c(Region, estimate)))
  names(TA_TO)[2] <- "TA_0"
  
  DIC_TO<-subset(DIC_coef, term=="(Intercept)")
  DIC_TO<-as.data.frame(select(DIC_TO, c(Region, estimate)))
  names(DIC_TO)[2] <- "DIC_0"
    
  Intercepts<-join(TA_TO, DIC_TO, by="Region", type="full")
  FLK.data<-join(FLK.data, Intercepts, by="Region", type="left")
```

```{r}
FLK.data$nTA<-(
    FLK.data$TA_umol_kg-FLK.data$TA_0)/
    FLK.data$BestSalinity*35+FLK.data$TA_0
  
  FLK.data$nDIC<-(
    FLK.data$DIC_umol_kg-FLK.data$DIC_0)/
    FLK.data$BestSalinity*35+FLK.data$DIC_0
  
#write.csv(FLK.data, "FLK_results/FLK.data_filtered_normalized.csv", row.names = F)
```

5. TA parameters to nTA

```{r}
kable(as.data.frame(TA_coef[,1:8], format = "markdown"), caption = "Table 1: TA parameters for normalization", digits = 3)

#write.csv(TA_coef, "TA_coef.csv")

```
    
```{r, echo=F, fig.height=8.8, fig.width=8.8}
# 5. Chech normalization?
nTA_Sal<- ggplot(FLK.data) + theme_bw() +
  #scale_y_continuous(limits = c(1700,2900),
  #                     name="TA",
  #                     breaks = seq(1800, 2800, 200),
  #                     expand = c(0, 0)) +
  # scale_x_continuous(name="Aragonite",
  #                limits = c(0.5,6),
  #                expand = c(0, 0),
  #                breaks = seq(1,6,1))+
  
geom_point(aes (BestSalinity, TA_umol_kg, fill=Season), alpha=0.5, shape=21)+
geom_smooth(aes(BestSalinity, TA_umol_kg), linetype=2, method = "lm", color="black")+
  
geom_point(aes (BestSalinity, nTA, fill=Season), alpha=0.5, shape=24)+
geom_smooth(aes(BestSalinity, nTA), linetype=1, method = "lm")+  

theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )
#nTA_Sal
#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

6. DIC parameters to nDIC

```{r}
    kable(as.data.frame(DIC_coef[,1:8], format = "markdown"), caption = "Table 2: DIC parameters for normalization", digits = 3)

#write.csv(DIC_coef, "DIC_coef.csv")
    
```

```{r, echo=F, fig.height=8.8, fig.width=8.8}
nDIC_Sal<- ggplot(FLK.data) + theme_bw() +
  #scale_y_continuous(limits = c(1700,2900),
  #                     name="TA",
  #                     breaks = seq(1800, 2800, 200),
  #                     expand = c(0, 0)) +
  # scale_x_continuous(name="Aragonite",
  #                limits = c(0.5,6),
  #                expand = c(0, 0),
  #                breaks = seq(1,6,1))+
  
geom_point(aes (BestSalinity, DIC_umol_kg, fill=Season),
           alpha=0.5, shape=21)+
geom_smooth(aes(BestSalinity, DIC_umol_kg),
            linetype=2, method = "lm", color="black")+
  
geom_point(aes (BestSalinity, nDIC, fill=Season), alpha=0.5, shape=24)+
geom_smooth(aes(BestSalinity, nDIC), linetype=1, method = "lm")+  

 
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )
#nDIC_Sal

#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

```{r,  echo=FALSE}
library(ggpubr)
FLK_parameters<-ggarrange(nTA_Sal, nDIC_Sal,
          #labels = c("DIC Friss regresion", "TA Friss regresion"),
          ncol = 2, nrow = 1)

FLK_parameters
```

**Figure 0:** Overview of linear regressions of total alkalinity (TA, µmol kg−1) and dissolved inorganic carbon (DIC, µmol kg−1) as a function of salinity + Friss normalized values.

* Original data: Black line and circles
* Friis normalization: blue line and triangles

# Discuss very low r2 in these corrections

# 4. nTA and nDIC relation

## 4.1 Region (all FLK samples)

```{r}
nTA_nDIC<- ggplot(FLK.data, aes (nDIC, nTA)) + 
  
  scale_y_continuous(#limits = c(1700,2900),
                     #expand = c(0, 0),
                     #breaks = seq(1800, 2800, 100),
                    name="nTA") +
  scale_x_continuous(# limits = c(1600, 2600),
                     # expand = c(0, 0),
                     # breaks = seq(1500,2600,100),
                      name="nDIC")+
MyTheme

#TA_DIC+ 
 #geom_point(aes (fill=Region, shape=Season), alpha=0.5)+
 #scale_shape_manual(values=c(21, 22, 23, 24))

#ggsave(file="Outputs/Figure_1_Experiment_design.svg", plot=Design, dpi = 300, width=6, height=4)
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_ext<-nTA_nDIC +
   scale_shape_manual(values=c(21,21,24, 24))+
  geom_point(aes (fill=Extreme, shape=Zone), alpha=0.4)+
  geom_smooth(method = "lm", colour="black")
 
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_pre<-nTA_nDIC +
  scale_shape_manual(values=c(21,21,24, 24))+
  geom_point(aes (fill=Precipitation,  shape=Zone), alpha=0.4)+
  geom_smooth(method = "lm", colour="black")
 
```

```{r}
nTA_nDIC_parameters<-ggarrange(nTA_nDIC_ext, nTA_nDIC_pre,
          #labels = c("DIC Friss regresion", "TA Friss regresion"),
          ncol = 2, nrow = 1)

nTA_nDIC_parameters
```

**Figure 2:** Linear regressions of total alkalinity (nTA) as a function of dissolved inorganic carbon (nDIC) for the Florida Keys.


```{r}
 # Individual LR for each region
    TA_DIC_lm <- FLK.data %>%
      group_by(Region) %>%
      do(mod = lm(nTA ~ nDIC, data = .))

    TA_DIC_coef <- FLK.data %>% 
                    group_by(Region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations", digits = 3)
```

## 4.2 By zone sub_region

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_ext_zone<-nTA_nDIC_ext + facet_grid(Zone~Sub_region)
nTA_nDIC_ext_zone
```

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_pre_zone<-nTA_nDIC_pre +  facet_grid(Zone~Sub_region)
nTA_nDIC_pre_zone
```

```{r}
 # Individual LR for each Zone and Sub_region
    TA_DIC_lm_zone <- FLK.data %>%
      group_by(Zone, Sub_region) %>%
      do(mod = lm(nTA ~ nDIC, data = .))

    TA_DIC_coef_zone <- FLK.data %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef_zone[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations", digits = 3)
```

**Notes: **

* Higher slopes in TA vs. DIC 
  * -> a higher NCC:NCP
  * -> calcifying (e.g., corals, sediments, and calcifying algae) relative to non-calcifying communities (e.g., fleshy algae)
  
* Intermediate slopes for mixed communities of calcifiers and non-calcifiers (Anthony et al., 2013; Page et al., 2016; Lantz et al., 2017). 


## 4.3 Removing Extreme events

```{r, fig.height=8.8, fig.width=8.8}
nTA_nDIC_Extreme<- ggplot() + 
    scale_y_continuous(#limits = c(1700,2900),
                     #expand = c(0, 0),
                     #breaks = seq(1800, 2800, 100),
                    name="nTA") +
  scale_x_continuous(# limits = c(1600, 2600),
                     # expand = c(0, 0),
                     # breaks = seq(1500,2600,100),
                      name="nDIC")+
  MyTheme +  facet_grid(Zone~Sub_region)+
  geom_smooth(data=FLK.data[FLK.data$Extreme=="Normal", ], 
              aes (nDIC, nTA), method = "lm", colour="black")

nTA_nDIC_Extreme + 
  geom_point(data=FLK.data, aes (nDIC, nTA, fill=Extreme), 
             shape=21, alpha=0.8)
```

# Discuss if including extreme events on nDIC nTA slopes

```{r}
nTA_nDIC_Extreme + 
  geom_point(data=FLK.data, aes (nDIC, nTA, fill=Precipitation), 
             shape=21, alpha=0.8)
```

**Figure 1:** Linear regressions of total alkalinity (nTA, µmol kg−1) and dissolved inorganic carbon (nDIC, µmol kg−1)

```{r}
 # Individual LR for each Zone and Sub_region
    
    TA_DIC_coef_zone_noExtremes <- FLK.data[FLK.data$Extreme=="Normal", ] %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(TA_DIC_coef_zone_noExtremes[,1:8], format = "markdown"),
          caption = "nTA vs nDIC equations without extreme events", digits = 3)
```

# Discuss  nTA - nDIC slope results

**Notes: **
* Inshore: UK has lowest slope- expected? 
* Mid Chanel: Biscayne and UK vs MK and LK- worth discussing? 

# 5. Basic plots and stats summary - Seasonality

## 5.1 Temperature

### Season stats 

```{r, echo=FALSE}
Temp.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Tmin = min (Temperature_C, na.rm = T), 
                Tmax = max (Temperature_C, na.rm = T),
                Tmean = mean (Temperature_C, na.rm = T), 
                Tsd = sd (Temperature_C, na.rm = T))

kable(as.data.frame(Temp.Season, format = "markdown"), caption = "Temperature by season")

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_All<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
Temperature_All +
  geom_point(aes (Date, Temperature_C, fill=Season), shape=21, alpha=0.8)

# Temperature_All +
#   geom_point(aes (Date, Temperature_C, fill=Extreme), shape=21, alpha=0.8) + facet_grid(Zone~.)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Temperature_month<- ggplot(FLK.data) +
  
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 40, 3),  
                       expand = c(0.1, 0.1)) +
  MyTheme +  facet_grid(Zone~Sub_region)
```

```{r}
Temperature_month +
  geom_boxplot(aes (x=Month, y=Temperature_C))+
  geom_point(aes (x=Month, y=Temperature_C, fill=Extreme), 
             shape=21, size = 1, alpha=0.5)
  
```

```{r}
Temperature_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=Temperature_C))+
  geom_point(aes (x=Month, y=Temperature_C, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
  
```

## 5.2 Salinity 

### Season stats 

```{r, echo=FALSE}
Sal.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Sal_min = min (BestSalinity, na.rm = T), 
                Sal_max = max (BestSalinity, na.rm = T),
                Sal_mean = mean (BestSalinity, na.rm = T), 
                Sal_sd = sd (BestSalinity, na.rm = T))

kable(as.data.frame(Sal.Season, format = "markdown"), caption = "Salinity by season")

```

### Overview

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
SAl_All<- ggplot(FLK.data) +
  scale_y_continuous(#limits = c(15,40),
                       name=(expression("Salinity")),
                       breaks = seq(15, 40, 2),  
                       expand = c(0.1, 0.1)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               #expand = c(0, 0),
               breaks ="6 months")+
  MyTheme 
SAl_All +
  geom_point(aes (Date, Temperature_C, fill=Season), shape=21, alpha=0.8)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_All<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(15,40),
                       #expand = c(0, 0),
                        name="Salinity",
                        breaks = seq(20, 40, 2)
                        ) +
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r}
Sal_All +
  geom_boxplot(aes (x=Month, y=BestSalinity))+
  geom_point(aes (x=Month, y=BestSalinity, fill=Extreme), 
             shape=21, size = 1, alpha=0.5)
```

```{r}
Sal_All +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=BestSalinity))+
  geom_point(aes (x=Month, y=BestSalinity, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```

!### Salinity - Temperature correlations and outliers

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Sal_Temp<- ggplot(FLK.data) + MyTheme+
  scale_x_continuous(limits = c(15,40),
                       name=(expression("Temperature"~(degree*C))),
                       breaks = seq(16, 36, 2),
                       expand = c(0, 0)) +
  scale_y_continuous(name="Salinity",
                 #limits = c(0.5,6),
                 #expand = c(0, 0),
                 breaks = seq(1,40,2))+
  geom_abline(slope = 0, intercept = 30, color="red", linetype=2)+
  geom_abline(slope = 0, intercept = 39, color="red", linetype=2)+
  geom_vline(xintercept = 33, color="red", linetype=2)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
# Sal_Temp +
#   geom_point(aes (Temperature_C, BestSalinity, fill=Precipitation),
#              alpha=0.5, shape=21)+
#   facet_wrap(~Zone)
#   
# Sal_Temp +  
#   geom_point(aes (Temperature_C, BestSalinity, fill=factor(Extreme)),
#              alpha=0.5, shape=21)+
#   facet_wrap(~Zone)
#   
# Sal_Temp +  
#   geom_point(aes (Temperature_C, BestSalinity, fill=factor(Year)),
#              alpha=0.5, shape=21)+
#   facet_wrap(~Zone)
```

## 5.3 Aragonite

### Season stats

```{r, echo=FALSE}
Aragonite.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                Amin = min (Aragonite_Sat_W, na.rm = T), 
                Amax = max (Aragonite_Sat_W, na.rm = T),
                Amean = mean (Aragonite_Sat_W, na.rm = T), 
                Asd = sd (Aragonite_Sat_W, na.rm = T))

kable(as.data.frame(Aragonite.Season, format = "markdown"), caption = "Omega by season")

Aragonite.Season.Subregion <- ddply (
  FLK.data, .(Season, Zone, Sub_region),summarise,
                Amin = min (Aragonite_Sat_W, na.rm = T), 
                Amax = max (Aragonite_Sat_W, na.rm = T),
                Amean = mean (Aragonite_Sat_W, na.rm = T), 
                Asd = sd (Aragonite_Sat_W, na.rm = T))

kable(as.data.frame(Aragonite.Season.Subregion, format = "markdown"), caption = "Omega by season and region")
```

### Overview

```{r,echo=FALSE, fig.height=8, fig.width=8.8}
Aragonite_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("Aragonite Saturation") ,
                       breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="6 months")+
    MyTheme +
    geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

Aragonite_all + 
  geom_point(aes (Date, Aragonite_Sat_W, fill=Season), shape=21, alpha=0.8)

```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
Omega_month<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("Aragonite saturation state "~Omega)),
                       breaks = seq(1, 5, 1),
                       expand = c(0.02, 0.02)
                        ) +
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)+
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r}
Omega_month +
  geom_boxplot(aes (x=Month, y=Aragonite_Sat_W))+
  geom_point(aes (x=Month, y=Aragonite_Sat_W, fill=Extreme), 
             shape=21, size = 1, alpha=0.5)
```

```{r}
Omega_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=Aragonite_Sat_W))+
  geom_point(aes (x=Month, y=Aragonite_Sat_W, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```

## 5.4 TA

### Season stats 

```{r, echo=FALSE}
nTA.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                nTAmin = min (nTA, na.rm = T), 
                nTAmax = max (nTA, na.rm = T),
                nTAmean = mean (nTA, na.rm = T), 
                nTAsd = sd (nTA, na.rm = T))

kable(as.data.frame(nTA.Season, format = "markdown"),
      caption = "nTA by season")

nTA.Season.Region <- ddply (FLK.data, .(Season, Zone, Sub_region),summarise,
                nTAmin = min (nTA, na.rm = T), 
                nTAmax = max (nTA, na.rm = T),
                nTAmean = mean (nTA, na.rm = T), 
                nTAsd = sd (nTA, na.rm = T))

kable(as.data.frame(nTA.Season.Region, format = "markdown"),
      caption = "nTA by season and region")
```

### Overview - outliers

```{r, echo=FALSE, fig.height=8.0, fig.width=8.8}
nTA_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("nTA") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
    #geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

nTA_all + 
  geom_point(aes (Date, nTA, fill=Season), shape=21, alpha=0.8)

```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_all + 
  geom_point(aes (Date, nTA, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 2400, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 2300, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2500, color="red", linetype=1)+
  facet_grid(Sub_region~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_month<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("nTA")),
                       breaks = seq(2000, 2800, 200),
                       expand = c(0.02, 0.02)
                        ) +
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_month +
  geom_boxplot(aes (x=Month, y=nTA))+
  geom_point(aes (x=Month, y=nTA, fill=Extreme), 
             shape=21, size = 1, alpha=0.5)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nTA_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=nTA))+
  geom_point(aes (x=Month, y=nTA, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```


## 5.5 DIC

### Season stats 

```{r, echo=FALSE}
nDIC.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                nDIC_min = min (nDIC, na.rm = T), 
                nDIC_max = max (nDIC, na.rm = T),
                nDIC_mean = mean (nDIC, na.rm = T), 
                nDIC_sd = sd (nDIC, na.rm = T))
kable(as.data.frame(nDIC.Season, format = "markdown"), caption = "DIC by season")

nDIC.Season.Region <- ddply (FLK.data, .(Season, Zone, Sub_region),summarise,
                nDIC_min = min (nDIC, na.rm = T), 
                nDIC_max = max (nDIC, na.rm = T),
                nDIC_mean = mean (nDIC, na.rm = T), 
                nDIC_sd = sd (nDIC, na.rm = T))
kable(as.data.frame(nDIC.Season.Region, format = "markdown"), caption = "nDIC by season")
```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
nDIC_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("nDIC") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
    #geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

nDIC_all + 
  geom_point(aes (Date, nDIC, fill=Season), shape=21, alpha=0.8)

```

```{r.  echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_all + 
  geom_point(aes (Date, nDIC, fill=Extreme), shape=21, alpha=0.8)+
  geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 2200, color="red", linetype=1)+
  geom_abline(slope = 0, intercept = 2000, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_month<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("nDIC")),
                       breaks = seq(2000, 2800, 200),
                       expand = c(0.02, 0.02)
                        ) +
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_month +
  geom_boxplot(aes (x=Month, y=nDIC))+
  geom_point(aes (x=Month, y=nDIC, fill=Extreme), 
             shape=21, size = 1, alpha=0.8)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
nDIC_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=nDIC))+
  geom_point(aes (x=Month, y=nDIC, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```

## 5.6 pCO2 

### Season stats 

```{r, echo=FALSE}
pCO2.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                pH_min = min (pCO2_uatm, na.rm = T), 
                pCO2_uatm_max = max (pCO2_uatm, na.rm = T),
                pCO2_uatm_mean = mean (pCO2_uatm, na.rm = T), 
                pCO2_uatm_sd = sd (pCO2_uatm, na.rm = T))
kable(as.data.frame(pCO2.Season, format = "markdown"), caption = "pCO2 by season")

pCO2.Season.Region <- ddply (FLK.data, .(Season, Zone, Sub_region),summarise,
                pH_min = min (pCO2_uatm, na.rm = T), 
                pCO2_uatm_max = max (pCO2_uatm, na.rm = T),
                pCO2_uatm_mean = mean (pCO2_uatm, na.rm = T), 
                pCO2_uatm_sd = sd (pCO2_uatm, na.rm = T))
kable(as.data.frame(pCO2.Season.Region, format = "markdown"), caption = "pCO2 by season")
```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
pCO2_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
  
pCO2_all + 
  geom_point(aes (Date, pCO2_uatm, fill=Season), shape=21, alpha=0.8)

```

```{r.  echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_all + 
  geom_point(aes (Date, pCO2_uatm, fill=Extreme), shape=21, alpha=0.8)+
  #geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 490, color="red", linetype=1)+
  #geom_abline(slope = 0, intercept = 2000, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_month<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("pCO2")),
                       breaks = seq(200, 600, 100),
                       expand = c(0.03, 0.03)
                        ) +
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_month +
  geom_boxplot(aes (x=Month, y=pCO2_uatm))+
  geom_point(aes (x=Month, y=pCO2_uatm, fill=Extreme), 
             shape=21, size = 1, alpha=0.8)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pCO2_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=pCO2_uatm))+
  geom_point(aes (x=Month, y=pCO2_uatm, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```

## 5.7 pH 

### Season stats 

```{r, echo=FALSE}
pH.Season <- ddply (FLK.data, .(Season, Zone),summarise,
                pH_min = min (pH_calculated, na.rm = T), 
                pCO2_uatm_max = max (pH_calculated, na.rm = T),
                pCO2_uatm_mean = mean (pH_calculated, na.rm = T), 
                pCO2_uatm_sd = sd (pH_calculated, na.rm = T))
kable(as.data.frame(pH.Season, format = "markdown"), caption = "pH  (calculated) by season")

pCO2.Season.Region <- ddply (FLK.data, .(Season, Zone, Sub_region),summarise,
                pH_min = min (pH_calculated, na.rm = T), 
                pCO2_uatm_max = max (pH_calculated, na.rm = T),
                pCO2_uatm_mean = mean (pH_calculated, na.rm = T), 
                pCO2_uatm_sd = sd (pH_calculated, na.rm = T))
kable(as.data.frame(pCO2.Season.Region, format = "markdown"), caption = "pH (calculated) by season")
```

### Overview - outliers

```{r,  echo=FALSE, fig.height=8.0, fig.width=8.8}
pH_all<- ggplot(FLK.data) +
    scale_y_continuous(#limits = c(0,5.5),
                       name=("pH - calculated") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
    scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.02, 0.02),
               breaks ="6 months")+
    MyTheme
  
pH_all + 
  geom_point(aes (Date, pH_calculated, fill=Season), shape=21, alpha=0.8)

```

```{r.  echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_all + 
  geom_point(aes (Date, pH_calculated, fill=Extreme), shape=21, alpha=0.8)+
  #geom_abline(slope = 0, intercept = 2100, color="gray", linetype=2)+
  geom_abline(slope = 0, intercept = 7.95, color="red", linetype=1)+
  #geom_abline(slope = 0, intercept = 2000, color="red", linetype=1)+
  facet_grid(~Zone)
```

### Monthly 

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_month<- ggplot(FLK.data) + 
   scale_y_continuous(#limits = c(1,5.5),
                       name=(expression ("pH")),
                       breaks = seq(0, 9, 0.1),
                       expand = c(0.03, 0.03)
                        ) +
  MyTheme +
  facet_grid(Zone~Sub_region)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_month +
  geom_boxplot(aes (x=Month, y=pH_calculated))+
  geom_point(aes (x=Month, y=pH_calculated, fill=Extreme), 
             shape=21, size = 1, alpha=0.8)
```

```{r, echo=FALSE, fig.height=8.8, fig.width=8.8}
pH_month +
  geom_boxplot(data=FLK.data[FLK.data$Extreme=="Normal", ], 
               aes (x=Month, y=pH_calculated))+
  geom_point(aes (x=Month, y=pH_calculated, fill=Precipitation), 
             shape=21, size = 1, alpha=0.5)
```

**Notes from Dereks' paper: **

* January 2010: High inshore TCO2 and TA in the UK after the cold-water mass mortality of reef-building corals that occurred at inshore patch reefs 
* August 2010: persistent winds at 5 to 7.5 m s21 and overcast skies during sampling. -> lower than normal nTA -> spike in pCO2 and depression in arag at both sites, erasing any inshore-to-offshore gradient for these two parameters
* October 2011:  high rainfall -> low salinity at all sites, with salinities inshore and offshore ranging from 32.04– 32.685 and 34.035–34.835, respectively. At the inshore sites, low salinity was coincident with a spike in pCO2 and depression in arag. All sites showed net respiration during this time

# 6 Remove extreme events

```{r}
FLK.data_filtered<-FLK.data[FLK.data$Extreme=="Normal",]
write.csv(FLK.data_filtered, "FLK.data_filtered2.csv", row.names = FALSE)
```

```{r, echo=FALSE}
Temp.Season <- ddply (FLK.data_filtered,
                     .(Zone, Sub_region, Season),summarise,
                mean = mean (Temperature_C, na.rm = T), 
                sd = sd (Temperature_C, na.rm = T))

Temp.Season <- gather(Temp.Season, statistics, value, mean:sd, factor_key=TRUE)
Temp.Season <- spread(Temp.Season, Season, value)

kable(as.data.frame(Temp.Season, format = "markdown"),
      caption = "Temperature by season, region and zone", digits=1)
```

```{r, echo=FALSE}
pCO2.Season <- ddply (FLK.data_filtered,
                     .(Zone, Sub_region, Season),summarise,
                mean = mean (pCO2_uatm, na.rm = T), 
                #med = median (pCO2_uatm, na.rm = T),
                sd = sd (pCO2_uatm, na.rm = T))

pCO2.Season <- gather(pCO2.Season, statistics, value, mean:sd, factor_key=TRUE)
pCO2.Season <- spread(pCO2.Season, Season, value)

kable(as.data.frame(pCO2.Season, format = "markdown"),
      caption = "pCO2 by season, region and zone", digits=1)
```

# 7 Oceanic-offshore corrections - SEASONAL PATTERNS WITH endpoint

```{r, echo=FALSE}
Cases_WS<-FLK.data_filtered %>% count(Month,
                            Sub_region,
                            Zone,
                            sort = F)
Cases_WS<-as.data.frame(Cases_WS %>%
                   pivot_wider(names_from = Month,
                   values_from = n))
#write.csv(Cases_WS, "Cases_WS.csv")


Cases_WS<-FLK.data_filtered %>% count(Year,
                            Sub_region,
                            Zone,
                            sort = F)

Cases_WS<-as.data.frame(Cases_WS %>%
                   pivot_wider(names_from = Year,
                   values_from = n))
#write.csv(Cases_WS, "Cases_WS.csv")

kable(as.data.frame(Cases_WS, format = "markdown"), 
      longtable = TRUE)

Cases_WS.MY<-FLK.data_filtered %>% count(MY,
                            Sub_region,
                            Zone,
                            sort = F)

Cases_WS.MY<-as.data.frame(Cases_WS.MY %>%
                   pivot_wider(names_from = MY,
                   values_from = n))

kable(as.data.frame(Cases_WS.MY, format = "markdown"), 
      longtable = TRUE)

```

## 7.1. nTA nDIC slopes

### 7.1.1 All nTA nDIC with mean oceanic-offshore value plotted for reference

**Option**: all values plotted individually, plus plot mean offshore oceanic for reference

```{r}
WS.open<-subset(FLK.data_filtered, FLK.data_filtered$Zone=="Offshore"|FLK.data_filtered$Zone=="Oceanic")

mean_Open<- ddply (WS.open, .(Sub_region),
                          summarise,
                nTA_O = mean (nTA, na.rm = T),
                nDIC_O = mean (nDIC, na.rm = T)
                )
mean_Open
```

```{r}
TA_DIC_Inshore<- ggplot(subset(FLK.data_filtered, Zone!="Mid channel"), 
                        aes (nDIC, nTA)) + 
  
  theme_bw() +
  scale_y_continuous(limits = c(1990,2810),
                     expand = c(0.01, 0.01),
                     breaks = seq(1800, 2800, 200),
                    name="nTA") +
  scale_x_continuous(limits = c(1790, 2410),
                      expand = c(0.01, 0.01),
                      breaks = seq(1800,2400,100),
                      name="nDIC")+
  
  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )+
  geom_point(aes (fill=Precipitation, shape=Zone),
             size=1, alpha=0.8)+
  scale_shape_manual(values=c(21, 24, 24))+
  
  geom_abline(slope = 0, intercept =mean_Open$nTA_O, 
              linetype=2, colour="gray")+
  geom_vline(xintercept = mean_Open$nDIC_O,
             linetype=2, colour="gray")+

  geom_point(data=mean_Open,
             aes (x=nDIC_O, y=nTA_O),
             size=3, alpha=1, shape=24, fill="black")+
  
  geom_smooth(data=subset(FLK.data_filtered, Zone=="Inshore"),
              method = "lm", colour="black") +
  facet_grid(~Sub_region)

```

```{r}
TA_DIC_Midchannel<- ggplot(subset(FLK.data_filtered, Zone!="Inshore"), 
                           aes (nDIC, nTA)) + 
  
  theme_bw() +
  scale_y_continuous(limits = c(1990,2810),
                     expand = c(0.01, 0.01),
                     breaks = seq(1800, 2800, 200),
                    name="nTA") +
  scale_x_continuous(limits = c(1790, 2410),
                      expand = c(0.01, 0.01),
                      breaks = seq(1800,2400,100),
                      name="nDIC")+
  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )+
  geom_point(aes (fill=Precipitation, shape=Zone),
             size=1, alpha=0.8)+
    scale_shape_manual(values=c(21, 24, 24))+
  
  geom_abline(slope = 0, intercept =mean_Open$nTA_O, 
              linetype=2, colour="gray")+
  geom_vline(xintercept = mean_Open$nDIC_O,
             linetype=2, colour="gray")+
  
  geom_point(data=mean_Open,
             aes (x=nDIC_O, y=nTA_O),
             size=3, alpha=1, shape=24, fill="black")+
    
  geom_smooth(data=subset(FLK.data_filtered, Zone=="Mid channel"),
              method = "lm", colour="black") +
  facet_grid(~Sub_region)

```

```{r}
FLK_slopes<-ggarrange(TA_DIC_Inshore,TA_DIC_Midchannel,
          labels = c("Inshore", "Midchannel"),
          ncol = 1, nrow = 2)

FLK_slopes

#ggsave(file="FLK_results/nTA_nDIC.svg", plot=FLK_slopes, dpi = 300, width=6, height=5.5)

```

Not my favorite, but good if absolute values are important vs value-reference

```{r}
 # Individual LR for each region
    
TA_DIC_lm_reef <- as.data.frame(FLK.data_filtered  %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(nTA~nDIC, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))}))        # get model info

    TA_DIC_lm_reef<-filter(TA_DIC_lm_reef, Zone!="Offshore")
    TA_DIC_lm_reef<-filter(TA_DIC_lm_reef, Zone!="Oceanic")

    kable(TA_DIC_lm_reef[,1:8], format = "markdown",
          caption = "nTA vs nDIC equations", digits = 3)
```

### 7.1.2 Delta de nTA and nDIC with endpoint calculated by each month-year

**Option**: Subset open water vs reefs and calculate mean ocean-offshore for each month-year

```{r}
  WS.open<-subset(FLK.data_filtered,
                  FLK.data_filtered$Zone=="Offshore"|
                    FLK.data_filtered$Zone=="Oceanic")
  WS.open$Date<-as.Date(WS.open$Date, "%Y-%m-%d")
 
  WS.reef<-subset(FLK.data_filtered, FLK.data_filtered$Zone=="Inshore"|FLK.data_filtered$Zone=="Mid channel")
  WS.reef$Date<-as.Date(WS.reef$Date, "%Y-%m-%d")
```

```{r}
# Get the oceanic / offshore mean values per month-year and subtract them from the reef data
nTA.MY.open <- ddply (WS.open, .(Sub_region, MY, Month),summarise,
                OnTA_my = mean (nTA, na.rm = T),
                sd = sd (nTA, na.rm = T),
                number = n())

nDIC.MY.open <- ddply (WS.open, .(Sub_region, MY, Month),summarise,
                OnDIC_my = mean (nDIC, na.rm = T),
                #sd = sd (nDIC, na.rm = T),
                number = n())

WS.reef<-join(WS.reef,nTA.MY.open[,-6], 
                 type = "left", by=c("MY", "Month", "Sub_region"))

WS.reef<-join(WS.reef, nDIC.MY.open, 
                 type = "left", by=c("MY", "Month", "Sub_region"))


# Delta nTA
WS.reef$dnTA_MY<-WS.reef$nTA-WS.reef$OnTA_my

# Delta nDIC
WS.reef$dnDIC_MY<-WS.reef$nDIC-WS.reef$OnDIC_my

```

```{r}
dnTA_dnDIC_my<- ggplot(WS.reef, aes (dnDIC_MY, dnTA_MY)) + 
  
  theme_bw() +
  scale_y_continuous(#limits = c(1700,2900),
                     #expand = c(0, 0),
                     #breaks = seq(1800, 2800, 100),
                    name=expression(Delta~"nTA")) +
  scale_x_continuous(# limits = c(1600, 2600),
                     # expand = c(0, 0),
                     # breaks = seq(1500,2600,100),
                      name=expression(Delta~"nDIC"))+
  
theme(legend.position="top",
          plot.background=element_blank(),
          axis.text.x = element_text(angle = 90, vjust = 0.5),
          panel.grid = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, 
                                         color = "black")
          )+

  geom_smooth(method = "lm", colour="black")+
  geom_abline(slope = 0, intercept = 0, linetype=2, colour="gray")+
  geom_vline(xintercept = 0, linetype=2, colour="gray")

Option2<-dnTA_dnDIC_my +
  geom_point(aes(fill=Precipitation), size=1, alpha=0.5, shape=21)+
  facet_grid(Zone~Sub_region)
Option2
#ggsave(file="FLK_results/nTA_nDIC_delta.svg", plot=Option2, dpi = 300, width=6, height=5)

```

```{r}
 # Individual LR for each region
   dnTA_dnDIC_lm_Subreg <- WS.reef %>% 
                    group_by(Zone, Sub_region) %>%
                    do({model = lm(dnTA_MY~dnDIC_MY, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(dnTA_dnDIC_lm_Subreg[,1:8], format = "markdown"),
          caption = "dnTA vs dnDIC equations (delta MY)", digits = 3)
    
    #write.csv(dnTA_dnDIC_lm_Subreg[,1:8], "FLK_results/nTA_nDIC_deltaMY.csv") 
```

* Higher slopes -> a higher NCC:NCP? = Lower and Middle keys, then Miami, then Upper keys

## 7.2 Seasonal - reef aragonite 

* Not corrected

```{r}
Aragonite_months<- ggplot(WS.reef,
                          aes(x=Month, y=Aragonite_Sat_W)) +
  
  MyTheme +
  scale_y_continuous(limits = c(2,5.5),
                       name=paste("Aragonite Saturation state (\u03a9)") ,
                       breaks = seq(2, 5, 0.5),  
                       expand = c(0, 0)) +
  geom_boxplot()+
  geom_point(aes(fill=Precipitation),
            shape=21, alpha=0.5, size=1)+ 
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)+
    
  facet_grid(Zone~Sub_region)
Aragonite_months
#ggsave(file="FLK_results/Aragonite_months_reef.svg", plot=Aragonite_months, dpi = 300, width=6, height=5)

```

```{r}
# Get the oceanic / offshore mean values per month-year and subtract them from the reef data
Omega.open <- ddply (WS.open, .(Sub_region, MY, Month),summarise,
                O_Arg_my = mean (Aragonite_Sat_W, na.rm = T))

WS.reef<-join(WS.reef, Omega.open[,-6], 
                 type = "left", by=c("MY", "Month", "Sub_region"))

# Delta Omega MY
WS.reef$dOmega_MY<-WS.reef$Aragonite_Sat_W-WS.reef$O_Arg_my
```

* Corrected ny month - year

```{r}
Aragonite_MY<- ggplot(WS.reef,
                          aes(x=Month, y=dOmega_MY)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(1.5,5.5),
                       name=expression (Delta~ "Aragonite Saturation state (\u03a9)") ,
                      # breaks = seq(2, 5, 1),  
                       expand = c(0.05, 0.05)) +
  geom_boxplot()+
  geom_point(aes(fill=Precipitation),
            shape=21, alpha=0.5, size=1)+ 
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
  facet_grid(Zone~Sub_region)
Aragonite_MY
#ggsave(file="FLK_results/Aragonite_months_reef.svg", plot=Aragonite_months, dpi = 300, width=6, height=5)

```

### Mean delta 

```{r, echo=FALSE}
dOmega.Season <- ddply (WS.reef, .(Season, Zone),summarise,
                dOm_min = min (dOmega_MY, na.rm = T), 
                dOm_uatm_max = max (dOmega_MY, na.rm = T),
                dOm_uatm_mean = mean (dOmega_MY, na.rm = T), 
                dOm_uatm_sd = sd (dOmega_MY, na.rm = T))
kable(as.data.frame(dOmega.Season, format = "markdown"), caption = "delta of Omega by season")

dOmega.Season.Region <- ddply (WS.reef, .(Season, Zone, Sub_region),summarise,
               dOm_min = min (dOmega_MY, na.rm = T), 
               dOm_uatm_max = max (dOmega_MY, na.rm = T),
               dOm_uatm_mean = mean (dOmega_MY, na.rm = T), 
               dOm_uatm_sd = sd (dOmega_MY, na.rm = T))
kable(as.data.frame(dOmega.Season.Region, format = "markdown"), caption = "delta of Omega by season")
```

## 7.3 seasonal delta nTA - MY

* delta nTA - MY

```{r}
dnTA_MY<- ggplot(WS.reef, aes(x=Month, y=dnTA_MY)) +
  MyTheme+
  scale_y_continuous(#limits = c(1,5.5),
                      name=(expression (Delta~ "nTA - MY")),
                       breaks = seq(-300, 200, 100),  
                       expand = c(0.05, 0.05)) +
  geom_boxplot()+
  geom_point(aes(fill=Season),
            shape=21, alpha=0.8, size=1)+ 
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
  facet_grid(Zone~Sub_region)
    
dnTA_MY
#ggsave(file="FLK_results/deltanTA_MY.svg", plot=dnTA_MY, dpi = 300, width=6, height=4.5)
```

### Mean delta 

```{r, echo=FALSE}
dTA.Season <- ddply (WS.reef, .(Season, Zone),summarise,
                dTA_min = min (dnTA_MY, na.rm = T), 
                dTA_uatm_max = max (dnTA_MY, na.rm = T),
                dTA_uatm_mean = mean (dnTA_MY, na.rm = T), 
                dTA_uatm_sd = sd (dnTA_MY, na.rm = T))
kable(as.data.frame(dTA.Season, format = "markdown"), caption = "delta of nTA by season")

dTA.Season.Region <- ddply (WS.reef, .(Season, Zone, Sub_region),summarise,
                dTA_min = min (dnTA_MY, na.rm = T), 
                dTA_uatm_max = max (dnTA_MY, na.rm = T),
                dTA_uatm_mean = mean (dnTA_MY, na.rm = T), 
                dTA_uatm_sd = sd (dnTA_MY, na.rm = T))
kable(as.data.frame(dTA.Season.Region, format = "markdown"), caption = "delta of nTA by season")
```

## 7.4 seasonal delta nDIC  - MY

* Delta nDIC - MY

```{r}
dnDIC_MY<- ggplot(WS.reef,aes(x=Month, y=dnDIC_MY)) +
  MyTheme+
  scale_y_continuous(#limits = c(1,5.5),
                       name=(expression (Delta~ "nDIC - Month-Year")),
                       breaks = seq(-300, 300, 100),   
                       expand = c(0.05, 0.05)) +
  geom_boxplot()+
  geom_point(aes(fill=Precipitation),
            shape=21, alpha=0.5, size=1)+ 
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
    
  facet_grid(Zone~Sub_region)
dnDIC_MY

#ggsave(file="FLK_results/deltanDIC_MY.svg", plot=dnDIC_MY, dpi = 300, width=6, height=4.5)
```

### Mean delta 

```{r, echo=FALSE}
dDIC.Season <- ddply (WS.reef, .(Season, Zone),summarise,
                dDIC_min = min (dnDIC_MY, na.rm = T), 
                dDIC_max = max (dnDIC_MY, na.rm = T),
                dDIC_mean = mean (dnDIC_MY, na.rm = T), 
                dDIC_sd = sd (dnDIC_MY, na.rm = T))
kable(as.data.frame(dDIC.Season, format = "markdown"), caption = "delta of nDIC by season")

dDIC.Season.Region <- ddply (WS.reef, .(Season, Zone, Sub_region),summarise,
               dDIC_min = min (dnDIC_MY, na.rm = T), 
                dDIC_max = max (dnDIC_MY, na.rm = T),
                dDIC_mean = mean (dnDIC_MY, na.rm = T), 
                dDIC_sd = sd (dnDIC_MY, na.rm = T))
kable(as.data.frame(dDIC.Season.Region, format = "markdown"), caption = "delta of nDIC by season")
```

***NOTES: **: Calfitication (delta nTA is kind of stable during summer and fall, but DIC (respiration?) increases during the fall and drops Omega?

# 8. Long Term trends in FLK (Al zones) using linear models

This approach is not optimum because of strong seasonality. Especially in the reef. However it is useful to compare the long term predictions with the ones from gam models. 

To deal with seasonality, include Season in the model. Month gets noisy since some month have been sampled very few times

## 8.1 Omega - all data

```{r}
Aragonite_all<- ggplot(FLK.data_filtered,
                          aes(x=Date, y=Aragonite_Sat_W)) +
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("Aragonite Saturation") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.02, 0.02)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.03, 0.03),
               breaks ="1 year")+

  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.8, size=1)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

Aragonite_all  
Aragonite_all + facet_grid(~Zone)
Aragonite_all + facet_grid(Sub_region~Zone)
#Aragonite_all + facet_grid(Zone~Precipitation)
```

Summer was not sampled in the early years!

## 8.2 nDIC - all data

```{r}
DIC_all<- ggplot(FLK.data_filtered,
                          aes(x=Date, y=nDIC)) +
  
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nDIC") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

   geom_smooth(method = "lm", color="black")+  
   geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.8, size=1)

DIC_all  
DIC_all + facet_grid(~Zone)
DIC_all + facet_grid(Sub_region~Zone)
```

## 8.3 nTA - all data

```{r}
nTA_all<- ggplot(FLK.data_filtered,
                          aes(x=Date, y=nTA)) +
  
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nTA") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
                 breaks ="1 year")+
  
  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.8, size=1)
nTA_all  
nTA_all + facet_grid(~Zone)
nTA_all + facet_grid(Zone~Sub_region)
```

## 8.5 pCO2

```{r}
pCO2_all<- ggplot(FLK.data_filtered,
                          aes(x=Date, y=pCO2_uatm)) +
  
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="2 year")+

  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.5, size=1)
pCO2_all
pCO2_all+ facet_grid(~Zone)
pCO2_all+ facet_grid(Zone~Sub_region)

```

## 8.6 pH

```{r}
pH_all<- ggplot(FLK.data_filtered,
                          aes(x=Date, y=pH_calculated)) +
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pH") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.01, 0.01)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="2 year")+

  geom_smooth(method = "lm", color="black")+  
  geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.5, size=1)
pH_all
pH_all+ facet_grid(~Zone)
pH_all+ facet_grid(Zone~Sub_region)
```

# 9 Omega LMERs

## 9.1 Omega - Open

### Raw data

```{r}
Aragonite_open <- ggplot(WS.open, aes(x=Date, y=Aragonite_Sat_W)) +
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("Aragonite Saturation - Offshore") ,
                       #breaks = seq(0, 5, 1),  
                      expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Sub_region))+  
  geom_point(aes(fill=factor(Precipitation)), shape=21, alpha=0.5)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

Aragonite_open 
Aragonite_open + facet_grid(~Precipitation)
Aragonite_open + facet_grid(~Season)
```

### Model

```{r}
Reference_LM<-lmer(Aragonite_Sat_W~Year * Season +
                                  #(1|Zone)+             
                                  #(1|Sub_region)+
                                  (1|SiteID), data=WS.open)
# Subregion is not significant

summary(Reference_LM)    
anova(Reference_LM)
ranova(Reference_LM)
#step(Reference_LM)

OmegaLM_Open<-lm(Aragonite_Sat_W~Year * Season, data=WS.open)
summary(OmegaLM_Open)    
anova(OmegaLM_Open)

par(mfrow=c(2,3))
plot(OmegaLM_Open)
acf(resid(OmegaLM_Open), main="acf(resid(Omega open))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.open$Season) ,
                        Year=seq(min(WS.open$Year), max(WS.open$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                         #Zone=unique(WS.open$Zone),
                        #Sub_region=unique(WS.open$Sub_region)
                          )
  

  pred_om_of <- data.frame(predict(OmegaLM_Open , newdata=NewData, se.fit = TRUE))
  pred_om_of <- transform(pred_om_of, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_om_of)
  
  pred_om_of<-cbind(NewData, pred_om_of)
  #pred_om_of$Year<-as.factor(pred_om_of$Year)
  
Aragonite_Open<- ggplot(pred_om_of,
                          aes(x=Year, y=fit, colour=Season)) +
  theme_bw() +
  scale_y_continuous(limits = c(2.8,4.6),
                       name=("Aragonite Saturation - Offshore") ,
                       breaks = seq(2.8, 4.8, 0.2),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'grey', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)+
    
  theme(legend.position="top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
            plot.background=element_blank(),
            axis.text.x = element_text(angle = 90, vjust = 0.5),
            panel.grid = element_blank(),
            legend.box.background = element_rect(),
            panel.background =element_rect(fill = NA, color = "black")
            )
Aragonite_Open
```


```{r}
Arg_off_lm <- WS.open %>% 
                    group_by(Season) %>%
                    do({model = lm(Aragonite_Sat_W~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(Arg_off_lm[,1:8], format = "markdown"),
          caption = "Offshore aragonite overtime", digits = 3)
```

Notes on Omega models: 
* declining omega for all month, but weird data in Feb 2012 bias this month regression
* data by season follows better GAM models

## 9.2 Omega - Inshore

### Raw data

```{r}
Aragonite_reef_data<- ggplot(WS.reef[WS.reef$Zone=="Inshore",],
                          aes(x=Date, y=Aragonite_Sat_W)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("Aragonite Saturation - Reef") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)
Aragonite_reef_data  
#Aragonite_reef_data  + facet_wrap(~Month)
Aragonite_reef_data+ facet_grid(~Precipitation)
Aragonite_reef_data + facet_grid(Zone~Sub_region)
Aragonite_reef_data + facet_grid(~Season)
```

### Model

```{r}
Arg_Reef<-lmer(Aragonite_Sat_W ~ Year * Season  +
                                  Sub_region +
                                  (1|SiteID),
               data=WS.reef[WS.reef$Zone=="Inshore", ])
# Subregion is not significant

summary(Arg_Reef)    
anova(Arg_Reef)
ranova(Arg_Reef)
#step(Arg_Reef)

OmegaLM_reef<-lm(Aragonite_Sat_W~Year + 
                  Season +
                  #Zone + Sub_region +
                  #Year:Zone + Year:Zone+
                  Year:Season, 
                  data=WS.reef[WS.reef$Zone=="Inshore", ])
summary(OmegaLM_reef)    
anova(OmegaLM_reef)

par(mfrow=c(2,3))
plot(OmegaLM_reef)
acf(resid(OmegaLM_reef), main="acf(resid(Omega open))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.reef$Season) ,
                        Year=seq(min(WS.reef$Year), max(WS.reef$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                        #Zone=unique(WS.reef$Zone),
                        #Sub_region=unique(WS.reef$Sub_region)
                        )
  

  pred_om_in <- data.frame(predict(OmegaLM_reef , newdata=NewData, se.fit = TRUE))
  pred_om_in <- transform(pred_om_in, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_om_in)
  
  pred_om_in<-cbind(NewData, pred_om_in)
  #pred_2$Year<-as.factor(pred_om_in$Year)
  
Aragonite_reef_m<- ggplot(pred_om_in,
                          aes(x=Year, y=fit, colour=Season)) +
  MyTheme +
  scale_y_continuous(limits = c(2.8,4.6),
                       name=("Aragonite Saturation - Reef") ,
                       breaks = seq(2.8, 4.8, 0.2),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)
    
Aragonite_reef_m 
#+ facet_grid(Zone~Sub_region)

```


```{r}
Arg_inn_lm <- WS.reef[WS.reef$Zone=="Inshore", ] %>% 
                    group_by(Season) %>%
                    do({model = lm(Aragonite_Sat_W~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(Arg_inn_lm[,1:8], format = "markdown"),
          caption = "Reef aragonite overtime", digits = 3)
```


## 9.3 Compare in and off-shore

```{r}
Omega_Models<-select(pred_om_of, c("Season", "Year", "fit"))
colnames(Omega_Models)<-c("Season", "Year", "offshore")
Omega_Models<-cbind(Omega_Models, pred_om_in[,3:4])
Omega_Models$Difference<-Omega_Models$fit-Omega_Models$offshore

#Omega_Models <- transform(Omega_Models, upper = Omega_Models + (2 * se.fit),
#                              lower = Omega_Models - (2 * se.fit))


Aragonite_diff<- ggplot(Omega_Models,
                          aes(x=Year, y=Difference, colour=Season)) +
  theme_bw() +
  scale_y_continuous(limits = c(-1,0.5),
                       name=("Aragonite Reef - Ocean") ,
                       breaks = seq(-1, 0.5, 0.2),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  #geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
    
  theme(legend.position="top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
            plot.background=element_blank(),
            axis.text.x = element_text(angle = 90, vjust = 0.5),
           panel.grid = element_blank(),
            legend.box.background = element_rect(),
            panel.background =element_rect(fill = NA, color = "black")
            )
Aragonite_diff 
#+ facet_grid(Zone~Sub_region)
```

```{r}
grid.arrange(Aragonite_Open, Aragonite_reef_m, Aragonite_diff, ncol=3)

```

# 10 nDIC LMERs

## 10.1 nDIC - Open

### Raw data

```{r}
nDIC_data_o<- ggplot(WS.open,
                          aes(x=Date, y=nDIC)) +
  
  MyTheme+
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nDIC -Offshore") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Sub_region))+  
  geom_point(aes(fill=factor(Month)), shape=21, alpha=0.5)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)

#nDIC_data_o + facet_wrap(~Month)
nDIC_data_o + facet_grid(~Zone)
nDIC_data_o+ facet_grid(~Precipitation)
nDIC_data_o+ facet_grid(~Season)
```

### Model

```{r}
nDICref_LM<-lmer(nDIC~Year * Season +
                                  #(1|Zone)+             
                                  #(1|Sub_region)+
                                  (1|SiteID), data=WS.open)
# Subregion and Site are not significant

summary(nDICref_LM)    
anova(nDICref_LM)
ranova(nDICref_LM)
#step(nDICref_LM)

nDICLM_Open<-lm(nDIC~Year * Season, data=WS.open)
summary(nDICLM_Open)    
anova(nDICLM_Open)

par(mfrow=c(2,3))
plot(nDICLM_Open)
acf(resid(nDICLM_Open), main="acf(resid(Omega open))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.open$Season) ,
                      Year=seq(min(WS.open$Year), max(WS.open$Year), by=1)#,
                      #SiteID=unique(WS.open$SiteID)#,
                       #Zone=unique(WS.open$Zone),
                      #Sub_region=unique(WS.open$Sub_region)
                          )
  

  pred_DIC_of <- data.frame(predict(nDICLM_Open , newdata=NewData, se.fit = TRUE))
  pred_DIC_of <- transform(pred_DIC_of, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_DIC_of)
  
  pred_DIC_of<-cbind(NewData, pred_DIC_of)
  #pred_DIC_of$Year<-as.factor(pred_DIC_of$Year)
  
nDIC_Open<- ggplot(pred_DIC_of,
                          aes(x=Year, y=fit, colour=Season)) +
  MyTheme+
  scale_y_continuous(limits = c(1900,2200),
                       name=("nDIC -Offshore") ,
                       breaks = seq(1900, 2200, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)
nDIC_Open
```


```{r}
nDIC_off_lm <- WS.open %>% 
                    group_by(Season) %>%
                    do({model = lm(nDIC~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(nDIC_off_lm[,1:8], format = "markdown"),
          caption = "Offshore aragonite overtime", digits = 3)
```

Notes on nDIC offshore models: 
* Spring and summer >0.05

## 10.2 nDIC - Inshore

### Raw data

```{r}
nDIC_reef_data<- ggplot(WS.reef[WS.reef$Zone=="Inshore",],
                          aes(x=Date, y=nDIC)) +
  
  MyTheme+
   scale_y_continuous(#limits = c(1950,2150),
                       name=("nDIC -Reefs") ,
                       breaks = seq(1700, 2500, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)
 
#nDIC_reef_data  + facet_wrap(~Month)
#Aragonite_reef + facet_grid(~Zone)
#nDIC_reef_data+ facet_grid(~Precipitation)
nDIC_reef_data + facet_grid(Zone~Sub_region)
nDIC_reef_data + facet_grid(~Season)
```

### Model

```{r}
nDIC_Reef<-lmer(nDIC~Year * Season + Sub_region+
                                  (1|SiteID),
                data=WS.reef[WS.reef$Zone=="Inshore",])
# Subregion is significant

summary(nDIC_Reef)    
anova(nDIC_Reef)
ranova(nDIC_Reef)
#step(nDIC_Reef)

nDICLM_reef<-lm(nDIC~Year + 
                  Season +
                  #Zone +
                  #Sub_region +
                  #Year:Zone + Year:Zone+
                  Year:Season, 
                  data=WS.reef[WS.reef$Zone=="Inshore",])
summary(nDICLM_reef)    
anova(nDICLM_reef)

par(mfrow=c(2,3))
plot(nDICLM_reef)
acf(resid(nDICLM_reef), main="acf(resid(nDIC-reef))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.reef$Season) ,
                        Year=seq(min(WS.reef$Year), max(WS.reef$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                        #Zone=unique(WS.reef$Zone),
                        #Sub_region=unique(WS.reef$Sub_region)
                        )
  

  pred_nDIC_in <- data.frame(predict(nDICLM_reef ,
                                     newdata=NewData, se.fit = TRUE))
  pred_nDIC_in <- transform(pred_nDIC_in, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_nDIC_in)
  
  pred_nDIC_in<-cbind(NewData, pred_nDIC_in)
 
nDIC_reef_m<- ggplot(pred_nDIC_in,
                     aes(x=Year, y=fit, colour=Season)) +
  MyTheme +
  scale_y_continuous(limits = c(1900,2200),
                       name=("nDIC -Reef") ,
                       breaks = seq(1900, 2200, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line()
nDIC_reef_m 
#+ facet_grid(Zone~Sub_region)

```


```{r}
nDIC_inn_lm <- WS.reef[WS.reef$Zone=="Inshore",]%>% 
                    group_by(Season) %>%
                    do({model = lm(nDIC~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(nDIC_inn_lm[,1:8], format = "markdown"),
          caption = "Reef aragonite overtime", digits = 3)
```

## 10.3 Compare in and off-shore

```{r}

nDIC_Models<-select(pred_DIC_of, c("Season", "Year", "fit"))
colnames(nDIC_Models)<-c("Season", "Year", "offshore")
nDIC_Models<-cbind(nDIC_Models, pred_nDIC_in[,3:4])
nDIC_Models$Difference<-nDIC_Models$fit-nDIC_Models$offshore

#Omega_Models <- transform(Omega_Models, upper = Omega_Models + (2 * se.fit),
#                              lower = Omega_Models - (2 * se.fit))


nDIC_diff<- ggplot(nDIC_Models,
                          aes(x=Year, y=Difference, colour=Season)) +
 MyTheme +
  scale_y_continuous(#limits = c(-1,0.5),
                       name=("nDIC Reef - Ocean") ,
                       breaks = seq(-100,100, 10),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  #geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)
nDIC_diff 
#+ facet_grid(Zone~Sub_region)
```

```{r}
grid.arrange(nDIC_Open, nDIC_reef_m, nDIC_diff, ncol=3)

```

# 11 nTA LMERs

## 11.1 nTA - Open

### Raw data

```{r}

nTA_data_o<- ggplot(WS.open,
                          aes(x=Date, y=nTA)) +
  
 MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("nTA -Offshore") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)

#nTA_data_o + facet_wrap(~Month)
nTA_data_o + facet_grid(~Zone)
nTA_data_o+ facet_grid(~Precipitation)
nTA_data_o+ facet_grid(~Season)

```

### Model

```{r}
nTAref_LM<-lmer(nTA~Year * Season +
                                  (1|Zone),             
                                  #(1|Sub_region),
                                  #(1|SiteID), 
                                  data=WS.open)
# Subregion is not significant

summary(nTAref_LM)    
anova(nTAref_LM)
ranova(nTAref_LM)
#step(nTAref_LM)

nTALM_Open<-lm(nTA~Year * Season, data=WS.open)
summary(nTALM_Open)    
anova(nTALM_Open)

par(mfrow=c(2,3))
plot(nTALM_Open)
acf(resid(nTALM_Open), main="acf(resid(nTA open))")
par(mfrow=c(1,1))
    
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                      Season=unique(WS.open$Season) ,
                      Year=seq(min(WS.open$Year), max(WS.open$Year), by=1)#,
                      #SiteID=unique(WS.open$SiteID)#,
                       #Zone=unique(WS.open$Zone),
                      #Sub_region=unique(WS.open$Sub_region)
                          )
  
  pred_TA_of <- data.frame(predict(nTALM_Open , newdata=NewData,
                                   se.fit = TRUE))
  pred_TA_of <- transform(pred_TA_of, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_TA_of)
  
  pred_TA_of<-cbind(NewData, pred_TA_of)
  #pred_TA_of$Year<-as.factor(pred_TA_of$Year)
  
nTA_Open<- ggplot(pred_TA_of,
                          aes(x=Year, y=fit, colour=Season)) +
  MyTheme +
  scale_y_continuous(limits = c(2200,2450),
                       name=("nTA - Open") ,
                       breaks = seq(2200, 2450, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line()
nTA_Open
```


```{r}
nTA_off_lm <- WS.open %>% 
                    group_by(Season) %>%
                    do({model = lm(nTA~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(nTA_off_lm[,1:8], format = "markdown"),
          caption = "Offshore aragonite overtime", digits = 3)
```

Notes on nTA offshore models: 
* year is not significant

## 11.2 nTA - Inshore

### Raw data

```{r}
nTA_reef_data<- ggplot(WS.reef[WS.reef$Zone=="Inshore", ] ,
                          aes(x=Date, y=nTA)) +
  
  MyTheme +
   scale_y_continuous(#limits = c(1950,2150),
                       name=("nTA -Reefs") ,
                       breaks = seq(1700, 2500, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)+
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)
nTA_reef_data
#nTA_reef_data  + facet_wrap(~Month)
nTA_reef_data + facet_grid(~Zone)
#nTA_reef_data+ facet_grid(~Precipitation)
#nTA_reef_data + facet_grid(Zone~Sub_region)
nTA_reef_data + facet_grid(~Season)
```

### Model

```{r}
nTA_Reef<-lmer(nTA~Year * Season +
                                  Sub_region+
                                  (1|SiteID),
               data=WS.reef[WS.reef$Zone=="Inshore", ])
# Subregion is not significant

summary(nTA_Reef)    
anova(nTA_Reef)
ranova(nTA_Reef)
#step(nTA_Reef)

nTALM_reef<-lm(nTA~Year + 
                  Season +
                  #Zone +
                  #Sub_region +
                  #Year:Zone + Year:Zone+
                  Year:Season, 
                  data=WS.reef[WS.reef$Zone=="Inshore", ])
summary(nTALM_reef)    
anova(nTALM_reef)

par(mfrow=c(2,3))
plot(nTALM_reef)
acf(resid(nTALM_reef), main="acf(resid(nTA-reef))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.reef$Season) ,
                        Year=seq(min(WS.reef$Year), max(WS.reef$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                        #Zone=unique(WS.reef$Zone),
                        #Sub_region=unique(WS.reef$Sub_region)
                        )
  

  pred_nTA_in <- data.frame(predict(nTALM_reef ,
                                     newdata=NewData, se.fit = TRUE))
  pred_nTA_in <- transform(pred_nTA_in, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_nTA_in)
  
  pred_nTA_in<-cbind(NewData, pred_nTA_in)
 
nTA_reef_m<- ggplot(pred_nTA_in,
                     aes(x=Year, y=fit, colour=Season)) +
  theme_bw() +
  scale_y_continuous(limits = c(2200,2450),
                       name=("nTA -Reef") ,
                       breaks = seq(2200, 2450, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 3, color="gray", linetype=2)+
    
  theme(legend.position="top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
            plot.background=element_blank(),
            axis.text.x = element_text(angle = 90, vjust = 0.5),
            panel.grid = element_blank(),
            legend.box.background = element_rect(),
            panel.background =element_rect(fill = NA, color = "black")
            )
nTA_reef_m 
#+ facet_grid(Zone~Sub_region)

```


```{r}
nTA_inn_lm <- WS.reef[WS.reef$Zone=="Inshore", ] %>% 
                    group_by(Season) %>%
                    do({model = lm(nTA~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(nTA_inn_lm[,1:8], format = "markdown"),
          caption = "Reef nTA overtime", digits = 3)
```

## 11.3 Compare in and off-shore


```{r}

nTA_Models<-select(pred_TA_of, c("Season", "Year", "fit"))
colnames(nTA_Models)<-c("Season", "Year", "offshore")
nTA_Models<-cbind(nTA_Models, pred_nTA_in[,3:4])
nTA_Models$Difference<-nTA_Models$fit-nTA_Models$offshore

nTA_diff<- ggplot(nTA_Models,
                          aes(x=Year, y=Difference, colour=Season)) +
  theme_bw() +
  scale_y_continuous(#limits = c(-1,0.5),
                       name=("nTA Reef - Ocean") ,
                       breaks = seq(-100,100, 10),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  #geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
    
  theme(legend.position="top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
            plot.background=element_blank(),
            axis.text.x = element_text(angle = 90, vjust = 0.5),
            panel.grid = element_blank(),
            legend.box.background = element_rect(),
            panel.background =element_rect(fill = NA, color = "black")
            )
nTA_diff 
#+ facet_grid(Zone~Sub_region)
```

```{r}
grid.arrange(nTA_Open, nTA_reef_m, nTA_diff, ncol=3)

```


# 12 pCO2 LMERs

## 12.1 pCO2 - Open

### Raw data

```{r}
pCO2_data_o<- ggplot(WS.open,
                          aes(x=Date, y=pCO2_uatm)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pCO2 -Offshore") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+
  
  geom_smooth(method = "lm", aes(colour=Sub_region))+  
  geom_point(aes(fill=factor(Month)), shape=21, alpha=0.5)
#pCO2_data_o + facet_wrap(~Month)
pCO2_data_o + facet_grid(~Zone)
pCO2_data_o+ facet_grid(~Precipitation)
pCO2_data_o+ facet_grid(~Season)
```

### Model

```{r}
pCO2ref_LM<-lmer(pCO2_uatm~Year * Season +
                                  (1|Zone)+             
                                  (1|Sub_region),
                                  #(1|SiteID), 
                                  data=WS.open)
# Subregion and zone are not significant

summary(pCO2ref_LM)    
anova(pCO2ref_LM)
ranova(pCO2ref_LM)
#step(pCO2ref_LM)

pCO2LM_Open<-lm(pCO2_uatm~Year * Season, data=WS.open)
summary(pCO2LM_Open)    
anova(pCO2LM_Open)

par(mfrow=c(2,3))
plot(pCO2LM_Open)
acf(resid(pCO2LM_Open), main="acf(resid(pCO2 open))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                      Season=unique(WS.open$Season) ,
                      Year=seq(min(WS.open$Year), max(WS.open$Year), by=1)#,
                      #SiteID=unique(WS.open$SiteID)#,
                       #Zone=unique(WS.open$Zone),
                      #Sub_region=unique(WS.open$Sub_region)
                          )
  
  pred_pCO2_of <- data.frame(predict(pCO2LM_Open , newdata=NewData,
                                   se.fit = TRUE))
  pred_pCO2_of <- transform(pred_pCO2_of, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_pCO2_of)
  
  pred_pCO2_of<-cbind(NewData, pred_pCO2_of)
  #pred_pCO2_of$Year<-as.factor(pred_pCO2_of$Year)
  
pCO2_Open<- ggplot(pred_pCO2_of,
                          aes(x=Year, y=fit, colour=Season)) +
  MyTheme+
  scale_y_continuous(limits = c(290,540),
                       name=("pCO2 -Offshore") ,
                      breaks = seq(290, 600, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line()
pCO2_Open
```


```{r}
pCO2_off_lm <- WS.open %>% 
                    group_by(Season) %>%
                    do({model = lm(pCO2_uatm~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(pCO2_off_lm[,1:8], format = "markdown"),
          caption = "Offshore pCO2 overtime", digits = 3)
```

Notes on pCO2 offshore models: 
* 

## 12.2 pCO2 - Inshore

### Raw data

```{r}
pCO2_reef_data<- ggplot(WS.reef[WS.reef$Zone=="Inshore", ],
                          aes(x=Date, y=pCO2_uatm)) +
  
    MyTheme+
   scale_y_continuous(#limits = c(1950,2150),
                       name=("pCO2 -Reefs") ,
                       breaks = seq(1700, 2500, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)
#pCO2_reef_data  + facet_wrap(~Month)
pCO2_reef_data + facet_grid(~Zone)
#pCO2_reef_data+ facet_grid(~Precipitation)
#pCO2_reef_data + facet_grid(Zone~Sub_region)
pCO2_reef_data + facet_grid(~Season)
```

### Model

```{r}
pCO2_Reef<-lmer(pCO2_uatm~Year * Season + Sub_region+
                                  (1|SiteID),
                data=WS.reef[WS.reef$Zone=="Inshore", ] )
# Subregion is not significant

#summary(pCO2_Reef)    
anova(pCO2_Reef)
ranova(pCO2_Reef)
#step(pCO2_Reef)

pCO2LM_reef<-lm(pCO2_uatm~Year + 
                  Season +
                  #Zone +
                  #Sub_region +
                  #Year:Zone + Year:Zone+
                  Year:Season, 
                  data=WS.reef[WS.reef$Zone=="Inshore", ] )
summary(pCO2LM_reef)    
anova(pCO2LM_reef)

par(mfrow=c(2,3))
plot(pCO2LM_reef)
acf(resid(pCO2LM_reef), main="acf(resid(pCO2-reef))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.reef$Season) ,
                        Year=seq(min(WS.reef$Year), max(WS.reef$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                        #Zone=unique(WS.reef$Zone),
                        #Sub_region=unique(WS.reef$Sub_region)
                        )
  

  pred_pCO2_in <- data.frame(predict(pCO2LM_reef ,
                                     newdata=NewData, se.fit = TRUE))
  pred_pCO2_in <- transform(pred_pCO2_in, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_pCO2_in)
  
  pred_pCO2_in<-cbind(NewData, pred_pCO2_in)
 
pCO2_reef_m<- ggplot(pred_pCO2_in,
                     aes(x=Year, y=fit, colour=Season)) +
  MyTheme+
  scale_y_continuous(limits = c(290,540),
                       name=("pCO2 -Reef") ,
                      breaks = seq(290, 600, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() 
pCO2_reef_m 
#+ facet_grid(Zone~Sub_region)

```


```{r}
pCO2_inn_lm <- WS.reef[WS.reef$Zone=="Inshore", ]  %>% 
                    group_by(Season) %>%
                    do({model = lm(pCO2_uatm~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(pCO2_inn_lm[,1:8], format = "markdown"),
          caption = "Reef pCO2 overtime", digits = 3)
```

## 12.3 Compare in and off-shore

```{r}
pCO2_Models<-select(pred_pCO2_of, c("Season", "Year", "fit"))
colnames(pCO2_Models)<-c("Season", "Year", "offshore")
pCO2_Models<-cbind(pCO2_Models, pred_pCO2_in[,3:4])
pCO2_Models$Difference<-pCO2_Models$fit-pCO2_Models$offshore

pCO2_diff<- ggplot(pCO2_Models,
                          aes(x=Year, y=Difference, colour=Season)) +
  theme_bw() +
  scale_y_continuous(#limits = c(-1,0.5),
                       name=("pCO2 Reef - Ocean") ,
                       breaks = seq(-100,150, 20),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  #geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)+
    
  theme(legend.position="top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
            plot.background=element_blank(),
            axis.text.x = element_text(angle = 90, vjust = 0.5),
            panel.grid = element_blank(),
            legend.box.background = element_rect(),
            panel.background =element_rect(fill = NA, color = "black")
            )
pCO2_diff 
#+ facet_grid(Zone~Sub_region)
```

```{r}
grid.arrange(pCO2_Open, pCO2_reef_m, pCO2_diff, ncol=3)

```

# 13 pH LMERs

## 13.1 pH - Open

### Raw data

```{r}
pH_data_o<- ggplot(WS.open,
                          aes(x=Date, y=pH_calculated)) +
  
  MyTheme +
  scale_y_continuous(#limits = c(0,5.5),
                       name=("pH -Offshore") ,
                       #breaks = seq(0, 5, 1),  
                       expand = c(0.03, 0.03)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.01, 0.01),
               breaks ="1 year")+

  geom_smooth(method = "lm", aes(colour=Sub_region))+  
  geom_point(aes(fill=factor(Sub_region)), shape=21, alpha=0.5)
pH_data_o
#pH_data_o + facet_grid(~Zone)
pH_data_o+ facet_grid(~Precipitation)
pH_data_o+ facet_grid(~Season)
```

### Model

```{r}
pHref_LM<-lmer(pH_calculated~Year * Season +
                                  (1|Zone)+             
                                  (1|Sub_region),
                                  #(1|SiteID), 
                                  data=WS.open)
# Subregion and zone are not significant

summary(pHref_LM)    
anova(pHref_LM)
ranova(pHref_LM)
#step(pHref_LM)

pHLM_Open<-lm(pH_calculated~Year * Season, data=WS.open)
summary(pHLM_Open)    
anova(pHLM_Open)

par(mfrow=c(2,3))
plot(pHLM_Open)
acf(resid(pHLM_Open), main="acf(resid(pH open))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                      Season=unique(WS.open$Season) ,
                      Year=seq(min(WS.open$Year), max(WS.open$Year), by=1)#,
                      #SiteID=unique(WS.open$SiteID)#,
                       #Zone=unique(WS.open$Zone),
                      #Sub_region=unique(WS.open$Sub_region)
                          )
  
  pred_pH_of <- data.frame(predict(pHLM_Open , newdata=NewData,
                                   se.fit = TRUE))
  pred_pH_of <- transform(pred_pH_of, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_pH_of)
  
  pred_pH_of<-cbind(NewData, pred_pH_of)
  #pred_pH_of$Year<-as.factor(pred_pH_of$Year)
  
pH_Open<- ggplot(pred_pH_of,
                          aes(x=Year, y=fit, colour=Season)) +
   MyTheme +
   scale_y_continuous(limits = c(7.9,8.2),
                         name=("pH -Offshore") ,
                        breaks = seq(7.9, 8.2, 0.1),  
                       expand = c(0.01, 0.01)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() 
pH_Open
```


```{r}
pH_off_lm <- WS.open %>% 
                    group_by(Season) %>%
                    do({model = lm(pH_calculated~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(pH_off_lm[,1:8], format = "markdown"),
          caption = "Offshore aragonite overtime", digits = 3)
```

Notes on pH offshore models: 
* 

## 13.2 pH - Inshore

### Raw data

```{r}
pH_reef_data<- ggplot(WS.reef[WS.reef$Zone=="Inshore", ],
                          aes(x=Date, y=pH_calculated)) +
  
   MyTheme +
   scale_y_continuous(#limits = c(1950,2150),
                       name=("pH -Reefs") ,
                       breaks = seq(1700, 2500, 50),  
                       expand = c(0.05, 0.05)) +
  scale_x_date(name="Date",
               #labels = date_format("%M/%Y"),
               #limits = c(-1,114),
               expand = c(0.05, 0.05),
               breaks ="1 year")+
  
  geom_smooth(method = "lm", aes(colour=Season))+  
  geom_point(aes(fill=factor(Season)), shape=21, alpha=0.5)
pH_reef_data
#Aragonite_reef + facet_grid(~Zone)
#pH_reef_data+ facet_grid(~Precipitation)
#pH_reef_data + facet_grid(Zone~Sub_region)
pH_reef_data + facet_grid(~Season)
```

### Model

```{r}
pH_Reef<-lmer(pH_calculated~Year * Season + Sub_region+
                                  (1|SiteID),
              data=WS.reef[WS.reef$Zone=="Inshore", ])
# Subregion is not significant

#summary(pH_Reef)    
anova(pH_Reef)
ranova(pH_Reef)
#step(pH_Reef)

pHLM_reef<-lm(pH_calculated~Year + 
                  Season +
                  #Zone +
                  #Sub_region +
                  #Year:Zone + Year:Zone+
                  Year:Season, 
                  data=WS.reef[WS.reef$Zone=="Inshore", ])
summary(pHLM_reef)    
anova(pHLM_reef)

par(mfrow=c(2,3))
plot(pHLM_reef)
acf(resid(pHLM_reef), main="acf(resid(pH-reef))")
par(mfrow=c(1,1))
```

### Predicted values

```{r}
# Create a new data frame for independent variables  
  NewData <- expand.grid(#Month=unique(WS.open$Month) ,
                        Season=unique(WS.reef$Season) ,
                        Year=seq(min(WS.reef$Year), max(WS.reef$Year), by=1)#,
                        #SiteID=unique(WS.open$SiteID)#,
                        #Zone=unique(WS.reef$Zone),
                        #Sub_region=unique(WS.reef$Sub_region)
                        )
  
  pred_pH_in <- data.frame(predict(pHLM_reef ,
                                     newdata=NewData, se.fit = TRUE))
  pred_pH_in <- transform(pred_pH_in, upper = fit + (2 * se.fit),
                              lower = fit - (2 * se.fit))
  head(pred_pH_in)
  
  pred_pH_in<-cbind(NewData, pred_pH_in)
 
  
pH_reef_m<- ggplot(pred_pH_in,
                     aes(x=Year, y=fit, colour=Season)) +
  MyTheme +
  scale_y_continuous(limits = c(7.9,8.2),
                       name=("pH -Reef") ,
                      breaks = seq(7.9, 8.2, 0.1),  
                       expand = c(0.01, 0.01)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() 
pH_reef_m 
#+ facet_grid(Zone~Sub_region)

```


```{r}
pH_inn_lm <- WS.reef[WS.reef$Zone=="Inshore", ] %>% 
                    group_by(Season) %>%
                    do({model = lm(pH_calculated~Year, data=.)  
                    # create model
                    data.frame(tidy(model), # get coefficient info
                    glance(model))})        # get model info

    kable(as.data.frame(pH_inn_lm[,1:8], format = "markdown"),
          caption = "Reef aragonite overtime", digits = 3)
```


## 13.3 Compare in and off-shore

```{r}
pH_Models<-select(pred_pH_of, c("Season", "Year", "fit"))
colnames(pH_Models)<-c("Season", "Year", "offshore")
pH_Models<-cbind(pH_Models, pred_pH_in[,3:4])
pH_Models$Difference<-pH_Models$fit-pH_Models$offshore

pH_diff<- ggplot(pH_Models,
                          aes(x=Year, y=Difference, colour=Season)) +
  MyTheme +
  scale_y_continuous(#limits = c(-1,0.5),
                       name=("pH Reef - Ocean") ,
                       breaks = seq(-100,150, 0.1),  
                       expand = c(0.05, 0.05)) +
  scale_x_continuous(name="Year",
               limits = c(2009,2020),
               expand = c(0, 0),
               breaks = seq(2009, 2020, by = 1))+

  #geom_ribbon(aes(ymin = lower, ymax = upper), fill = 'gray', alpha = 0.5) +
  geom_line() +
  geom_abline(slope = 0, intercept = 0, color="gray", linetype=2)
pH_diff 
#+ facet_grid(Zone~Sub_region)
```

```{r}
grid.arrange(pH_Open, pH_reef_m, pH_diff, ncol=3)

```


## Manzello (2012)

* local carbonate chemistry: Variation on CO2, alkalinity, and salinity - Florida Reef Tract (FRT) data.

* Measure total CO2 (TCO2) - coulometrically and total alkalinity (TA) - gran titration. Other parameters derived 
* Predominantly in inshore / upper FRT (higher than modeled). 
* H Productivity -> net uptake of total CO2 (TCO2) -> H aragonite
*Offshore reefs: oceanic carbonate chemistries consistent with present day tropical surface ocean conditions.
* Photosynthetic uptake of TCO2 by seagrasses/macroalgae in the inshore waters of the FRT. Acidification refugia (spatial * time)

## Uthicke (2014)

* GBR - 14 Inshore fringing  reefs
Measured: TA and DIC. Derived:pCO2, pH and aragonite
* TA: 2069 - 2364 mmol kg2
* DIC:1846 - 2099 mmol kg2
* pCO2: 340 - 554 matm
  * Higher wet seasons
  * Inshore reefs above atmospheric values.
  * Arg was not further reduced in the wet season (temp effects)
  *Thermodynamic effects and anthropogenic runoff (P, R and P/R ratios).
  * Expected slope of  linear regression bw DIC and TA in systems where calcification is dominating is ~ 2.0 
  
## Cyronak (2018)

* Net community production; NCP - organic
* net community calcification; NCC inorganic
* 23 coral reef locations across the globe - derived from TA and DIC
* All reefs were net calcifying for the majority of observations (alkalinity depletion relative to offshore)
* Occasional observations of net dissolution occurred at most locations
* Influence of organic carbon fluxes on total changes in dissolved inorganic carbon (DIC) (i.e., NCP compared to the sum of NCP and NCC) =  32% to 88% -> biogeochemical differences between reefs. 
* Reefs with the largest relative percentage of NCP experienced the largest variability in seawater pH for a given change in DIC -> ability to elevate or suppress local pH relative to the open ocean.

## Ian (2019) 

* Reefs and inlets were sampled
* Reefs: Elevated pCO2 in warmer wet season
* Inlets: more dynamic -> periodic pulses of acidified water -> more acidification than reefs. 
  - Negative correlation bw salinity and both TA, and DIC. Elevated TA and DIC in low salinity waters ->  carbonate dissolution as a result of organic matter decomposition?.
  
  

